### 2024-12-05 report/paper/draft.tex
initial commit

\documentclass{article}

% if you need to pass options to natbib, use, e.g.:
%     \PassOptionsToPackage{numbers, compress}{natbib}
% before loading neurips_2024

% ready for submission
\usepackage[final]{neurips_2024}

% to compile a preprint version, e.g., for submission to arXiv, add add the
% [preprint] option:
%     \usepackage[preprint]{neurips_2024}

% to compile a camera-ready version, add the [final] option, e.g.:
%     \usepackage[final]{neurips_2024}

% to avoid loading the natbib package, add option nonatbib:
%    \usepackage[nonatbib]{neurips_2024}

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{xcolor}         % colors
\usepackage{graphicx}       % graphics (added by Jeffery)
\usepackage{float}          % float (added by Jeffery)

\title{ UMD Building Classification Proposal }

\author{%
  Can Li \\
  \texttt{c5405@umd.edu} \\
  \And 
  Jeffery Tian \\
  \texttt{jtian12@umd.edu} \\
  \And 
  Jerry Li\\
  \texttt{jli103@umd.edu} \\
  \And 
  Christopher Lim \\
  \texttt{clim0326@umd.edu} \\
  \And 
  Justin Zhao \\
  \texttt{justinfz@umd.edu} \\
}

\begin{document}

\maketitle

\begin{abstract}
  We propose that, given an input image of a UMD building, we can classify the building with the correct name in close to realtime using CNN image segmentation and classification methods. What makes this project valuable for educational purposes is that we will explore how to build our image database from scratch, experiment with different convolution neural networks, different ways to visualize the CNN layers for debugging our network design and potentially even for segmentation, and utilizing semi-supervised learning.
\end{abstract}

\section{Motivation}
\label{motivation}

The primary motivator for this project lies in the challenge of combined segmentation of multiple buildings in an image and the subsequent classification of them, while also segmenting and accounting for foreground blocking objects (eg. pedestrians, trees, cars). While from a purely practical standpoint it's true that buildings are mapped (eg. Google Maps) already, this still represents a strong "AR-like" result.

\subsection{Related Works}

Much work has been done with relation to image segmentation of multiple relevant objects (eg. buildings) and their classification.

\begin{itemize}
    \item On the topic of image recognition/classification, AlexNet, VGG, and Resnet are strong examples of traditional CNN recognition and classification models. We intend to build on their techniques.
    \item With respect to image segmentation, we may end up using Grad-CAM/Score-CAM as detailed after this section. However, we will compare with traditional segmentation techniques as detailed in class (proposals and culling, and we can implement something similar to U-Net)
\end{itemize}

This also includes significant work being done on visual explanations of CNN models via Selvaraju, et al.\ (2019) Grad-CAM and other related works. These can be used as an alternative method of segmentation and recognition. Below we discuss the main works of relevance to our work:

% Write: how gradcam can help find the location of the building in the image (to help find its not on the foreground images), point out how this isn't the case in prelim

\begin{itemize} % IP: Gradcam, Scorecam, Gradcam++
    \item Grad-CAM, Selvaraju, et al.\ (2019), uses the final gradient into the last convolution layer to produce a visual representation of strength in decision making. This is a visual indicator of model strength and is on paper highly useful for highlighting image classification confidence, but can also be used to help define segmentation. 
    % https://arxiv.org/abs/1610.02391 gradcam
    \item Grad-CAM++, Chattopadhay, et al.\ (2018) is an upgrade to Grad-CAM by generalizing it. It can then isolate/identify multiple object instances in a single image (important for our proposal due to the presence of multiple buildings in images) and a generally improved visual indicator. 
    % https://arxiv.org/abs/1710.11063 gradcam++
    \item Score-CAM, Wang, et al.\ (2020) is an alternative approach to Grad-CAM that completely discards using the gradient and instead evaluates the weight of each activation map in the forward pass. 
    % https://arxiv.org/abs/1910.01279 scorecam
\end{itemize}

Grad-CAM++ and Score-CAM can both be used as an important means for highlighting image classification confidence, both of which we intend to use as the most advanced methods in their respective lineages. As an example, see our preliminary original Grad-CAM results in Figure 1 on instances on our test set, where Grad-CAM indicates it's making predictions based on unrelated objects (foreground foliage, people, unrelated elements of the building). This can be used for confirmation of model confidence. If the model is sufficiently confident, this can even be used as a means to indicate building locations (especially given Grad-CAM++ ability to find multiple instances) within the image rather than using traditional segmentation techniques.

Figure 2 (attached to the appendix) has examples utilizing Grad-CAM++ on architecture similar to ResNet.

\begin{figure}
    \centering
    \includegraphics[width=0.3\linewidth]{fig1.png}
    \caption{Preliminary Grad-CAM results}
    \label{fig:prelim_results_1}
\end{figure}

\subsection{Motivation for Proposed Methods}

From these prior works we have the basic motivation of leveraging traditional CNN image segmentation and recognition techniques for the sake of identifying any buildings in the input images. Our main innovation is to attempt to use Grad-CAM++ or a similar technique to see if they can be used for image segmentation instead, and to attempt to apply this basic system to a variety of goals.

\section{Proposed Approach}
\label{approach}

\subsection{Data Collection}

All data will be collected by group members individually. We plan to select a set of UMD buildings (at least 10-15) for the classification. Each building will have at least 50 images taken using our phones from different angles, distances, and lighting (eg. time of day). We plan to do data augmentation for the buildings.

Preprocessing will be done to normalize/resize images to a standard, strip metadata, and we will also consider color segmenting the building out of the image (eg. filtering out possible noise from the sky/foreground, although this will have the detriment of making it less robust). We also consider using alternative encodings; HSV may help given the UMD red-brown brick style

Should the dataset be large, it can be proposed to train multiple models and utilize model averaging/ensemble voting to merge.

\subsection{Paradigm}

We intend to use a CNN architecture, loosely based around existing methods, in a semi-supervised format. We can use MeanTeacher or FixMatch for the method of semi-supervised learning.

It's also possible to use a graph based method and a GNN. It would be interesting to attempt this by using labeled/unlabled samples as nodes, and should this perform reasonably this can be used as a primary paradigm as well.

Training can be done on Google Colab, but we also have the option of using a training server (SAIL @ Columbia)

\section{Expected Plan}
\label{plan}

\subsection{Timeline}

\begin{enumerate}
    \item Nov 1 - We intend to have the dataset ready. At the time of writing we have \verb|~|1k photos before augmentation and processing.
    \item Mid Nov - We want to ensure we have image classification trained correctly on building recognition for simple cases (single buildings with noise and on various conditions). 
    \item End Nov - Hyper parameter tuning/Grad-CAM++/Score-CAM visualizations to improve the performance of the CNN architecture. Ensure via Grad-CAM that the model is confident and attempt preliminary segmentation on multiple instances and find confidence.
    \item December - Utilize alternative segmentation methods (Grad-CAM/Score-CAM lineage) and alternative architecture (GNNs) and compare with our results.
\end{enumerate}

Note - preliminary results indicate that Score-CAM may be too slow to be ideal on our set.

% chronological plans

\subsection{Moonshot Goals}

% Show a 3D version of the UMD building given by a 2D image as input.
% Take all images of all UMD buildings, including the building interiors, for classification.
% Based on our database of images, generate an image that represents UMD building styles using diffusion models.
% video?\

We have a variety of higher level goals for our project beyond just the basic plan. \begin{itemize}
    \item First, should our model performance be tuned to be sufficiently fast, we would like to be able to apply it to videos. Sampling a video at 5-10 fps and passing it through the video is a simple way to accomplish this given enough performance.
    \item Being able to classify all buildings on UMD (there are a lot of them) rather than just those in the central dataset. 
    \item Being able to identify architectural styles beyond just building names. If the model is sufficiently confident we could even write a model to generate representative images of UMD architecture using a diffusion model (a long shot because it requires massive architecture changes)
    \item Reconstruct a 3-D model of the building using a 2-D model as input (eg. not just classification but an understanding of what the building actually looks like - this is a long shot because it would likely require a lot of data and huge paradigm changes)
    \item Interior identification of buildings (much harder due to a potential lack of distinguishing features)
\end{itemize}

\newpage 
\appendix

\section{Extra Figures}

\begin{figure}[H]
    \centering
    \includegraphics[width=1\linewidth]{fig2.png}
    \caption{Preliminary Results with structure from ResNet}
    \label{fig:prelim_results_2}
\end{figure}

\section*{References}
\label{cites}

\medskip

{
\small

% Cite format MLA 9 - Jeffery
[1] Krizhevsky, Alex, et al. “ImageNet Classification with Deep Convolutional Neural Networks.” Communications of the ACM, vol. 60, no. 6, May 2012, pp. 84–90, proceedings.neurips.cc/paper\_files/paper/2012/file/c399862d3b9d6b76c8436e924a68c45b-Paper.pdf.

[2] Simonyan, Karen, and Andrew Zisserman. “Very Deep Convolutional Networks for Large-Scale Image Recognition.” ArXiv.org, 10 Apr. 2015, arxiv.org/abs/1409.1556.

[3] He, Kaiming, et al. “Deep Residual Learning for Image Recognition.” ArXiv.org, arXiv, 10 Dec. 2015, arxiv.org/abs/1512.03385.

[4] Selvaraju, Ramprasaath R., et al. “Grad-CAM: Visual Explanations from Deep Networks via Gradient-Based Localization.” International Journal of Computer Vision, vol. 128, no. 2, Feb. 2020, pp. 336–59, https://doi.org/10.1007/s11263-019-01228-7.

[5] Chattopadhay, Aditya, et al. “Grad-CAM++: Generalized Gradient-Based Visual Explanations for Deep Convolutional Networks.” 2018 IEEE Winter Conference on Applications of Computer Vision (WACV), Mar. 2018, https://doi.org/10.1109/wacv.2018.00097.

[6] Wang, Haofan, et al. “Score-CAM: Score-Weighted Visual Explanations for Convolutional Neural Networks.” ArXiv:1910.01279 [Cs], Apr. 2020, arxiv.org/abs/1910.01279.

\end{document}

### 2024-12-05 slic/slic.py

@@ -1,0 +1,52 @@
+import PIL.Image
+import numpy as np
+import matplotlib.pyplot as plt
+from sklearn.datasets import fetch_openml
+from skimage.segmentation import slic
+from skimage import color
+from skimage.util import img_as_float
+import cv2
+import PIL
+from torch_geometric.data import Data
+
+from utils import *
+
+# ------------------- SLIC ------------------- #
+IMAGE_DIR = './'
+SIZE = (224, 224)
+N_SEGMENTS = 500
+COMPACTNESS = 1
+
+print('Loading data...')
+
+# Load images from the directory
+images = load_dir(IMAGE_DIR)  # Replace with the path to your image directory
+images = [cv2.resize(image, SIZE) for image in images]
+
+sample_image = images[0]
+
+slicified = slicify(sample_image, n_segments=N_SEGMENTS, compactness=COMPACTNESS, radius=SIZE[0]//8, max_neighbors=32)
+
+print(slicified)
+
+slicified_image = superpixels_to_2d_image(rec=slicified, scale=10, edge_width=5, size_tuple=SIZE, bg=sample_image)
+slicified_graph = superpixels_to_2d_image(rec=slicified, scale=10, edge_width=5, size_tuple=SIZE, bg=None)
+
+# plot the 3 images
+plt.figure(figsize=(15, 15))
+plt.subplot(131)
+plt.imshow(sample_image)
+plt.title('Original Image')
+plt.axis('off')
+
+plt.subplot(132)
+plt.imshow(slicified_image)
+plt.title('Superpixels')
+plt.axis('off')
+
+plt.subplot(133)
+plt.imshow(slicified_graph)
+plt.title('Graph Connectivity')
+plt.axis('off')
+
+plt.show()

### 2024-12-05 slic/utils.py

@@ -1,0 +1,85 @@
+import torch
+import numpy as np
+import cv2
+import os
+import torchvision.transforms as T
+from torch_geometric.data import Data
+from torch_geometric.transforms import ToSLIC, RadiusGraph
+
+# Function to load images from the directory
+def load_dir(path: str) -> np.ndarray:
+    # Get all *.png, *.jpg, *.jpeg files in the directory
+    files = [f for f in os.listdir(path) if f.endswith('.png') or f.endswith('.jpg') or f.endswith('.jpeg')]
+    images = []
+    for file in files:
+        image = cv2.imread(os.path.join(path, file))
+        # Convert to RGB
+        image = cv2.cvtColor(image, cv2.COLOR_BGR2RGB)
+        images.append(image)
+    return np.array(images)
+
+# Function to convert superpixels to a 2D image using torch_geometric Data format
+def superpixels_to_2d_image(rec: Data, bg, scale: int = 30, edge_width: int = 1, size_tuple: tuple = (224,224)) -> np.ndarray:
+    # Scale the positions of the superpixels
+    rect_expand = scale * 5
+    pos = (rec.pos.clone() * scale).int()
+    new_size = (size_tuple[0] * scale, size_tuple[1] * scale)
+    # Create a blank image to display the superpixels
+    if bg is not None:
+        bg_resized = cv2.resize(bg, new_size, interpolation=cv2.INTER_LINEAR)
+        image = bg_resized.copy()
+    else:
+        image = np.full((*new_size, 3), fill_value=255, dtype=np.uint8) 
+    
+    # Draw superpixels as rectangles on the image
+    for (color, (x, y)) in zip(rec.x, pos):
+        x0, y0 = int(x), int(y)
+        x1, y1 = x0 - rect_expand//2, y0 - rect_expand//2
+        x0, y0 = x0 + rect_expand//2, y0 + rect_expand//2
+        if x1 < 0:
+            x1 = 0
+        if y1 < 0:
+            y1 = 0
+        if x0 >= new_size[0]:
+            x0 = new_size[0] - 1
+        if y0 >= new_size[1]:
+            y0 = new_size[1] - 1
+        
+        # Ensure color is a tensor with 3 elements (RGB)
+        color = color.numpy()  # Convert tensor to NumPy array
+        color = (color * 255).round().astype(np.uint8)
+        color = tuple(color.tolist())  # Convert to RGB tuple
[…]

### 2024-12-05 slic/scripts/train.py
changes

@@ -1,0 +1,126 @@
+from typing import Callable, cast
+
+import click
+import torch
+import wandb
+from torch.utils.data import DataLoader
+
+from gnn_image_classification.datasets import build_train_val_dataloaders
+from gnn_image_classification.model import GNNImageClassificator
+
+
+def train_one_epoch(
+    model: GNNImageClassificator,
+    optimizer: torch.optim.Optimizer,
+    train_loader: DataLoader,
+    criterion: Callable,
+    batches_passed: int,
+) -> int:
+    model.train()
+    for batch in train_loader:
+        batch_node_features = batch["batch_node_features"]
+        batch_edge_indices = batch["batch_edge_indices"]
+        classes = batch["classes"]
+
+        logits = model(batch_node_features=batch_node_features, batch_edge_indices=batch_edge_indices)
+        predicted_classes = torch.argmax(logits, dim=1)
+
+        loss = criterion(logits, classes).mean()
+
+        optimizer.zero_grad()
+        loss.backward()
+        optimizer.step()
+
+        accuracy = (predicted_classes == classes).to(torch.float32).mean()
+
+        wandb.log({
+            "train_accuracy": float(accuracy.detach().cpu().numpy()),
+            "train_loss": float(loss.detach().cpu().numpy()),
+            "batch": batches_passed,
+        })
+
+        batches_passed += 1
+
+    return batches_passed
+
+
+@torch.no_grad()
+def evaluate(
+    model: GNNImageClassificator,
+    val_loader: DataLoader,
+    epochs_passed: int,
+) -> None:
+    model.eval()
+
+    accuracy_sum: float = 0.0
+    num_samples: int = 0
+
+    for batch in val_loader:
+        batch_node_features = batch["batch_node_features"]
+        batch_edge_indices = batch["batch_edge_indices"]
+        classes = batch["classes"]
+
+        logits = model(batch_node_features=batch_node_features, batch_edge_indices=batch_edge_indices)
+        predicted_classes = torch.argmax(logits, dim=1)
+
+        accuracy_sum += float((predicted_classes == classes).to(torch.float32).mean().cpu().numpy()) * len(classes)
+        num_samples += len(classes)
+
+    accuracy = accuracy_sum / num_samples
+
+    wandb.log({
+        "val_accuracy": accuracy,
+        "epoch": epochs_passed,
+    })
+
+
+@click.command()
+@click.option("--batch-size", type=int, default=64)
[…]

### 2024-12-05 slic/slic.py

@@ -12,10 +12,15 @@ from torch_geometric.data import Data
 from utils import *
 
 # ------------------- SLIC ------------------- #
-IMAGE_DIR = './'
+IMAGE_DIR = './in/'
 SIZE = (224, 224)
-N_SEGMENTS = 500
-COMPACTNESS = 1
+N_SEGMENTS = 750
+COMPACTNESS = .5
+RADIUS_FACTOR = 1/8
+MAX_NEIGHBORS = 32
+
+SCALE = 10
+EDGE_WIDTH = 5
 
 print('Loading data...')
 
@@ -23,30 +28,31 @@ print('Loading data...')
 images = load_dir(IMAGE_DIR)  # Replace with the path to your image directory
 images = [cv2.resize(image, SIZE) for image in images]
 
-sample_image = images[0]
+for sample_image, i in zip(images, range(len(images))):
+    slicified = slicify(sample_image, n_segments=N_SEGMENTS, compactness=COMPACTNESS, radius=SIZE[0]*RADIUS_FACTOR, max_neighbors=MAX_NEIGHBORS)
 
-slicified = slicify(sample_image, n_segments=N_SEGMENTS, compactness=COMPACTNESS, radius=SIZE[0]//8, max_neighbors=32)
+    print(slicified)
 
-print(slicified)
+    slicified_image = superpixels_to_2d_image(rec=slicified, scale=SCALE, edge_width=EDGE_WIDTH, size_tuple=SIZE, bg=sample_image)
+    slicified_graph = superpixels_to_2d_image(rec=slicified, scale=SCALE, edge_width=EDGE_WIDTH, size_tuple=SIZE, bg=None)
 
-slicified_image = superpixels_to_2d_image(rec=slicified, scale=10, edge_width=5, size_tuple=SIZE, bg=sample_image)
-slicified_graph = superpixels_to_2d_image(rec=slicified, scale=10, edge_width=5, size_tuple=SIZE, bg=None)
+    # plot the 3 images
+    plt.figure(figsize=(15, 5))
+    plt.subplot(131)
+    plt.imshow(sample_image)
+    plt.title('Original Image')
+    plt.axis('off')
 
-# plot the 3 images
-plt.figure(figsize=(15, 15))
-plt.subplot(131)
-plt.imshow(sample_image)
-plt.title('Original Image')
-plt.axis('off')
+    plt.subplot(132)
+    plt.imshow(slicified_image)
[…]

### 2024-12-05 slic/utils.py

@@ -83,3 +83,14 @@ def slicify(image: np.ndarray, n_segments: int = 50, compactness: int = 10, radi
     )
     data = transform(image)
     return data
+
+def slicify_images(images: np.ndarray, n_segments: int = 50, compactness: int = 10, radius: float = 10.0, max_neighbors: int = 32) -> list:
+    transform = T.Compose(
+        [
+            T.ToTensor(), 
+            ToSLIC(n_segments=n_segments, compactness=compactness),
+            RadiusGraph(r=radius, max_num_neighbors=max_neighbors)
+        ]
+    )
+    data_list = [transform(image) for image in images]
+    return data_list

### 2024-12-05 code/my_fixmatch/models/wideresnet.py
added code and output files, need one more code file

@@ -1,0 +1,127 @@
+# code from https://github.com/kekmodel/FixMatch-pytorch/blob/master/models/wideresnet.py
+
+import logging
+
+import torch
+import torch.nn as nn
+import torch.nn.functional as F
+
+logger = logging.getLogger(__name__)
+
+
+def mish(x):
+    """Mish: A Self Regularized Non-Monotonic Neural Activation Function (https://arxiv.org/abs/1908.08681)"""
+    return x * torch.tanh(F.softplus(x))
+
+
+class PSBatchNorm2d(nn.BatchNorm2d):
+    """How Does BN Increase Collapsed Neural Network Filters? (https://arxiv.org/abs/2001.11216)"""
+
+    def __init__(self, num_features, alpha=0.1, eps=1e-05, momentum=0.001, affine=True, track_running_stats=True):
+        super().__init__(num_features, eps, momentum, affine, track_running_stats)
+        self.alpha = alpha
+
+    def forward(self, x):
+        return super().forward(x) + self.alpha
+
+
+class BasicBlock(nn.Module):
+    def __init__(self, in_planes, out_planes, stride, drop_rate=0.0, activate_before_residual=False):
+        super(BasicBlock, self).__init__()
+        self.bn1 = nn.BatchNorm2d(in_planes, momentum=0.001)
+        self.relu1 = nn.LeakyReLU(negative_slope=0.1, inplace=True)
+        self.conv1 = nn.Conv2d(in_planes, out_planes, kernel_size=3, stride=stride,
+                               padding=1, bias=False)
+        self.bn2 = nn.BatchNorm2d(out_planes, momentum=0.001)
+        self.relu2 = nn.LeakyReLU(negative_slope=0.1, inplace=True)
+        self.conv2 = nn.Conv2d(out_planes, out_planes, kernel_size=3, stride=1,
+                               padding=1, bias=False)
+        self.drop_rate = drop_rate
+        self.equalInOut = (in_planes == out_planes)
+        self.convShortcut = (not self.equalInOut) and nn.Conv2d(in_planes, out_planes, kernel_size=1, stride=stride,
+                                                                padding=0, bias=False) or None
+        self.activate_before_residual = activate_before_residual
+
+    def forward(self, x):
+        if not self.equalInOut and self.activate_before_residual == True:
+            x = self.relu1(self.bn1(x))
+        else:
+            out = self.relu1(self.bn1(x))
[…]

### 2024-12-05 dataset.py

@@ -1,98 +1,0 @@
-import os
-import torch
-from PIL import Image
-from torch.utils.data import Dataset
-
-
-class LabeledDataset(Dataset):
-    def __init__(self, folder_path, classes, transform=None):
-        """
-        Args:
-            folder_path (str): Path to the folder containing labeled images
-            and subdirectories.
-
-            classes (list): List of class keywords.
-
-            transform (callable, optional):
-            Optional transform to apply to images.
-        """
-        self.folder_path = folder_path
-        self.classes = classes
-        self.transform = transform
-
-        # Recursively collect all image paths from subdirectories
-        self.image_paths = []
-        for root, _, files in os.walk(folder_path):
-            for file in files:
-                if file.endswith((".jpg", ".jpeg", ".JPG")):
-                    self.image_paths.append(os.path.join(root, file))
-
-
-    def __len__(self):
-        return len(self.image_paths)
-
-    def __getitem__(self, idx):
-        # Load image
-        img_path = self.image_paths[idx]
-        image = Image.open(img_path).convert("RGB")
-
-        # Extract class label from filename
-        label = None
-        for i, cls in enumerate(self.classes):
-            if cls in os.path.basename(img_path):
-                label = i
-                break
-
-        if label is None:
-            raise ValueError(f"Class label not found in file name: {img_path}")
-
-        # Apply transforms
-        if self.transform:
-            image = self.transform(image)
-
-        return image, torch.tensor(label, dtype=torch.long)
-
-
-# class LabeledDataset(Dataset):
-#     def __init__(self, root_dir, class_keywords, transform=None):
-#         """
-#         Args:
-#             root_dir (str): Path to the dataset directory (train, val, or test).
-#             class_keywords (list): List of class keywords corresponding to subfolder names.
-#             transform (callable, optional): Optional transform to be applied on an image.
-#         """
-#         self.root_dir = root_dir
-#         self.class_keywords = class_keywords
-#         self.transform = transform
-
-#         # Create a list of all image paths and their corresponding labels
-#         self.image_paths = []
-#         self.labels = []
-#         for class_index, class_name in enumerate(class_keywords):
-#             class_dir = os.path.join(root_dir, class_name)
-#             if not os.path.exists(class_dir):
-#                 raise ValueError(f"Class directory '{class_dir}' not found in {root_dir}")
-#             for filename in os.listdir(class_dir):
[…]

### 2024-12-05 old_code/dataset.py

@@ -1,0 +1,98 @@
+import os
+import torch
+from PIL import Image
+from torch.utils.data import Dataset
+
+
+class LabeledDataset(Dataset):
+    def __init__(self, folder_path, classes, transform=None):
+        """
+        Args:
+            folder_path (str): Path to the folder containing labeled images
+            and subdirectories.
+
+            classes (list): List of class keywords.
+
+            transform (callable, optional):
+            Optional transform to apply to images.
+        """
+        self.folder_path = folder_path
+        self.classes = classes
+        self.transform = transform
+
+        # Recursively collect all image paths from subdirectories
+        self.image_paths = []
+        for root, _, files in os.walk(folder_path):
+            for file in files:
+                if file.endswith((".jpg", ".jpeg", ".JPG")):
+                    self.image_paths.append(os.path.join(root, file))
+
+
+    def __len__(self):
+        return len(self.image_paths)
+
+    def __getitem__(self, idx):
+        # Load image
+        img_path = self.image_paths[idx]
+        image = Image.open(img_path).convert("RGB")
+
+        # Extract class label from filename
+        label = None
+        for i, cls in enumerate(self.classes):
+            if cls in os.path.basename(img_path):
+                label = i
+                break
+
+        if label is None:
+            raise ValueError(f"Class label not found in file name: {img_path}")
+
+        # Apply transforms
+        if self.transform:
+            image = self.transform(image)
+
+        return image, torch.tensor(label, dtype=torch.long)
+
+
+# class LabeledDataset(Dataset):
+#     def __init__(self, root_dir, class_keywords, transform=None):
+#         """
+#         Args:
+#             root_dir (str): Path to the dataset directory (train, val, or test).
+#             class_keywords (list): List of class keywords corresponding to subfolder names.
+#             transform (callable, optional): Optional transform to be applied on an image.
+#         """
+#         self.root_dir = root_dir
+#         self.class_keywords = class_keywords
+#         self.transform = transform
+
+#         # Create a list of all image paths and their corresponding labels
+#         self.image_paths = []
+#         self.labels = []
+#         for class_index, class_name in enumerate(class_keywords):
+#             class_dir = os.path.join(root_dir, class_name)
+#             if not os.path.exists(class_dir):
+#                 raise ValueError(f"Class directory '{class_dir}' not found in {root_dir}")
+#             for filename in os.listdir(class_dir):
[…]

### 2024-12-05 old_code/run.sh

@@ -1,0 +1,7 @@
+python train.py \
+    --model_name resnet50 \
+    --num_classes 11 \
+    --train_data "..\photos\train" \
+    --val_data "..\photos\validation" \
+    --test_data "..\photos\test" \
+    --pretrained

### 2024-12-05 old_code/train.py

@@ -1,0 +1,233 @@
+import argparse
+import os
+import torch
+import torch.nn as nn
+import torch.optim as optim
+import matplotlib.pyplot as plt
+import numpy as np
+import cv2
+
+from cam import *
+from models import get_model #our models 
+from dataset import LabeledDataset
+from torch.utils.data import DataLoader
+from torchvision import transforms
+from tqdm import tqdm # for progress bar stuff
+
+# If you don't like the layout of the code, fix it. Appriciated :)
+
+#TODO: If the code is wrong, fix it
+
+class Config: #TODO: might change something here
+    DEVICE = torch.device("cuda" if torch.cuda.is_available() else "cpu")
+    MODEL_NAME = "resnet18"
+    EPOCHS = 10
+    LR = 0.001
+    BATCH_SIZE = 32
+    CLASS_KEYWORDS = [
+    "art_sociology",
+    "atlantic",
+    "brendan_iribe",
+    "esj",
+    "farm",
+    "mckeldinlib",
+    "physics",
+    "prince_frederick",
+    "reckord_armory",
+    "regents_drive",
+    "yahentamitsi_dinning"]
+
+def train_with_metrics(model, 
+                       train_loader, 
+                       val_loader, 
+                       test_loader, 
+                       criterion, 
+                       optimizer, 
+                       config, 
+                       checkpoint_path="checkpoint.pth"):
+    
+    metrics = {"train_acc": [], "val_acc": []}
+    best_val_acc = 0.0
+    start_epoch = 0
+
+    # Check if checkpoint exists
+    if os.path.exists(checkpoint_path):
+        print(f"Resuming from checkpoint: {checkpoint_path}")
+        checkpoint = torch.load(checkpoint_path)
+        model.load_state_dict(checkpoint['model_state'])
+        optimizer.load_state_dict(checkpoint['optimizer_state'])
+        start_epoch = checkpoint['epoch'] + 1
+        metrics = checkpoint['metrics']
+        best_val_acc = checkpoint['best_val_acc']
+
+    # Training epoch starts here...
+    for epoch in range(start_epoch, config.EPOCHS):
+        model.train()
+        train_loss, correct, total = 0.0, 0, 0
+
+        # Training phase
+        for images, labels in tqdm(train_loader, desc=f"Epoch {epoch+1}/{config.EPOCHS} [Training]"):
[…]

### 2024-12-05 run.sh

@@ -1,7 +1,0 @@
-python train.py \
-    --model_name resnet50 \
-    --num_classes 11 \
-    --train_data "..\photos\train" \
-    --val_data "..\photos\validation" \
-    --test_data "..\photos\test" \
-    --pretrained

### 2024-12-08 cam.py
aug scripts

@@ -1,114 +1,0 @@
-import numpy as np
-import torch
-import cv2
-import warnings
-# Suppress FutureWarnings
-warnings.filterwarnings("ignore", category=FutureWarning, message="Using a non-full backward hook when the forward contains multiple autograd Nodes is deprecated")
-
-#This is for visualizing the 
-#If you find this code not good, fix it please. Appriciated.
-
-class GradCAM:
-    def __init__(self, model, target_layer):
-        self.model = model
-        self.target_layer = target_layer
-        self.gradients = None
-        self.hook()
-
-    def hook(self):
-        def forward_hook(module, input, output):
-            self.features = output
-
-        def backward_hook(module, grad_in, grad_out):
-            self.gradients = grad_out[0]
-
-        target_layer = dict(self.model.named_modules())[self.target_layer]
-        target_layer.register_forward_hook(forward_hook)
-        target_layer.register_backward_hook(backward_hook)
-
-    def generate(self, input_tensor, target_class):
-        model_output = self.model(input_tensor)
-        self.model.zero_grad()
-
-        one_hot_output = torch.zeros((1, model_output.size()[-1])).to(device)
-        one_hot_output[0][target_class] = 1
-        model_output.backward(gradient=one_hot_output)
-
-        grad = self.gradients.data.cpu().numpy()[0]
-        features = self.features.data.cpu().numpy()[0]
-        weights = np.mean(grad, axis=(1, 2))
-
-        # generate cam
-        cam = np.zeros(features.shape[1:], dtype=np.float32)
-
-        for i, w in enumerate(weights):
-            cam += w * features[i]
-
-        cam = np.maximum(cam, 0)
-
-        # Normalize the CAM
-        cam = cam - np.min(cam)  # Shift the values to make the minimum zero
-        eps = 1e-7  # Small value to prevent division by zero
-        cam = cam / (np.max(cam) + eps)  # Normalize the CAM
-        cam = np.nan_to_num(cam)  # Replace NaNs with zeros if any
-
-        # Resize CAM to match the input image size
-        cam = cv2.resize(cam, (448, 448))
-
-        return cam
-    
-
-class GradCAMPlusPlus:
-    def __init__(self, model, target_layer):
-        self.model = model
-        self.target_layer = target_layer
-        self.gradients = None
-        self.activations = None
-        self.hook()
-
-    def hook(self):
-        def forward_hook(module, input, output):
[…]

### 2024-12-08 code/my_fixmatch/models/ema.py

@@ -1,0 +1,37 @@
+from copy import deepcopy
+
+import torch
+
+class ModelEMA(object):
+    def __init__(self, device, model, decay):
+        self.ema = deepcopy(model)
+        self.ema.to(device)
+        self.ema.eval()
+        self.decay = decay
+        self.ema_has_module = hasattr(self.ema, 'module')
+        # Fix EMA. https://github.com/valencebond/FixMatch_pytorch thank you!
+        self.param_keys = [k for k, _ in self.ema.named_parameters()]
+        self.buffer_keys = [k for k, _ in self.ema.named_buffers()]
+        for p in self.ema.parameters():
+            p.requires_grad_(False)
+
+    def update(self, model):
+        needs_module = hasattr(model, 'module') and not self.ema_has_module
+        with torch.no_grad():
+            msd = model.state_dict()
+            esd = self.ema.state_dict()
+            for k in self.param_keys:
+                if needs_module:
+                    j = 'module.' + k
+                else:
+                    j = k
+                model_v = msd[j].detach()
+                ema_v = esd[k]
+                esd[k].copy_(ema_v * self.decay + (1. - self.decay) * model_v)
+
+            for k in self.buffer_keys:
+                if needs_module:
+                    j = 'module.' + k
+                else:
+                    j = k
+                esd[k].copy_(msd[j])

### 2024-12-08 code/my_fixmatch/utils/misc.py

@@ -1,0 +1,44 @@
+# code from https://github.com/kekmodel/FixMatch-pytorch/tree/master
+
+import logging
+
+logger = logging.getLogger(__name__)
+
+__all__ = ['accuracy', 'AverageMeter']
+
+
+def accuracy(output, target, topk=(1,)):
+    """Computes the precision@k for the specified values of k"""
+    maxk = max(topk)
+    batch_size = target.size(0)
+
+    _, pred = output.topk(maxk, 1, True, True)
+    pred = pred.t()
+    correct = pred.eq(target.reshape(1, -1).expand_as(pred))
+
+    res = []
+    for k in topk:
+        correct_k = correct[:k].reshape(-1).float().sum(0)
+        res.append(correct_k.mul_(100.0 / batch_size))
+    return res
+
+
+class AverageMeter(object):
+    """Computes and stores the average and current value
+       Imported from https://github.com/pytorch/examples/blob/master/imagenet/main.py#L247-L262
+    """
+
+    def __init__(self):
+        self.reset()
+
+    def reset(self):
+        self.val = 0
+        self.avg = 0
+        self.sum = 0
+        self.count = 0
+
+    def update(self, val, n=1):
+        self.val = val
+        self.sum += val * n
+        self.count += n
+        self.avg = self.sum / self.count

### 2024-12-08 misc/aug/assets/extra/collate.py

@@ -1,0 +1,25 @@
+import os
+import shutil
+
+# Define the source and destination directories
+source_dir = './'
+destination_dir = os.path.join(source_dir, 'total')
+print("Target directory: ", destination_dir)
+
+# Create the destination directory if it doesn't exist
+if not os.path.exists(destination_dir):
+    os.makedirs(destination_dir)
+
+# Iterate through all folders in the source directory
+for folder_name in os.listdir(source_dir):
+    folder_path = os.path.join(source_dir, folder_name)
+
+    # Check if it is a directory
+    if os.path.isdir(folder_path):
+        # Iterate through all files in the folder
+        for file_name in os.listdir(folder_path):
+            file_path = os.path.join(folder_path, file_name)
+
+            # Copy each file to the destination directory if the file is not already there
+            if os.path.isfile(file_path) and not os.path.exists(os.path.join(destination_dir, file_name)):
+                shutil.copy(file_path, destination_dir)

### 2024-12-08 misc/aug/core/data_loader.py

@@ -1,0 +1,232 @@
+from pathlib import Path
+from itertools import chain
+import os
+import random
+
+from munch import Munch
+from PIL import Image
+import numpy as np
+
+import torch
+from torch.utils import data
+from torch.utils.data.sampler import WeightedRandomSampler
+from torchvision import transforms
+from torchvision.datasets import ImageFolder
+
+def listdir(dname):
+    fnames = list(chain(*[list(Path(dname).rglob('*.' + ext))
+                          for ext in ['png', 'jpg', 'jpeg', 'JPG']]))
+    return fnames
+
+
+class DefaultDataset(data.Dataset):
+    def __init__(self, root, transform=None):
+        self.samples = listdir(root)
+        self.samples.sort()
+        self.transform = transform
+        self.targets = None
+
+    def __getitem__(self, index):
+        fname = self.samples[index]
+        img = Image.open(fname).convert('RGB')
+        if self.transform is not None:
+            img = self.transform(img)
+        return img
+
+    def __len__(self):
+        return len(self.samples)
+
+
+class ReferenceDataset(data.Dataset):
+    def __init__(self, root, transform=None):
+        self.samples, self.targets = self._make_dataset(root)
+        self.transform = transform
+
+    def _make_dataset(self, root):
+        domains = os.listdir(root)
+        fnames, fnames2, labels = [], [], []
+        for idx, domain in enumerate(sorted(domains)):
+            class_dir = os.path.join(root, domain)
+            cls_fnames = listdir(class_dir)
+            fnames += cls_fnames
+            fnames2 += cls_fnames #random.sample(cls_fnames, len(cls_fnames))
+            labels += [idx] * len(cls_fnames)
+        return list(zip(fnames, fnames2)), labels
+
+    def __getitem__(self, index):
+        fname, fname2 = self.samples[index]
+        label = self.targets[index]
+        img = Image.open(fname).convert('RGB')
+        img2 = Image.open(fname2).convert('RGB')
+        if self.transform is not None:
+            img = self.transform(img)
+            img2 = self.transform(img2)
+        return img, img2, label
+
+    def __len__(self):
+        return len(self.targets)
+
+
+def _make_balanced_sampler(labels):
+    class_counts = np.bincount(labels)
+    class_weights = 1. / class_counts
+    weights = class_weights[labels]
+    return WeightedRandomSampler(weights, len(weights))
+
+
[…]

### 2024-12-08 misc/aug/core/solver.py

@@ -1,0 +1,356 @@
+import os
+from os.path import join as ospj
+import time
+import datetime
+from munch import Munch
+import torch
+import torch.nn as nn
+import torch.nn.functional as F
+from tqdm import tqdm
+from core.model import build_model
+from core.checkpoint import CheckpointIO
+from core.data_loader import InputFetcher
+import core.utils as utils
+import glob
+
+class Solver(nn.Module):
+    def __init__(self, args):
+        super().__init__()
+        self.args = args
+        self.device = torch.device('cuda' if torch.cuda.is_available() else 'cpu')
+        self.nets, self.nets_ema = build_model(args)
+
+        for name, module in self.nets.items():
+            utils.print_network(module, name)
+            setattr(self, name, module)
+        for name, module in self.nets_ema.items():
+            setattr(self, name + '_ema', module)
+
+        if args.mode == 'train':
+            self.optims = Munch()
+            for net in self.nets.keys():
+                if net == 'fan':
+                    continue
+                self.optims[net] = torch.optim.Adam(
+                    params=self.nets[net].parameters(),
+                    lr=args.f_lr if net == 'mapping_network' else args.lr,
+                    betas=[args.beta1, args.beta2],
+                    weight_decay=args.weight_decay)
+
+            self.ckptios = [
+                CheckpointIO(ospj(args.checkpoint_dir, '{:06d}_nets.ckpt'), **self.nets),
+                CheckpointIO(ospj(args.checkpoint_dir, '{:06d}_nets_ema.ckpt'), **self.nets_ema),
+                CheckpointIO(ospj(args.checkpoint_dir, '{:06d}_optims.ckpt'), **self.optims)]
+        else:
+            print(ospj(args.checkpoint_dir, '{:06d}_nets_ema.ckpt'.format(args.resume_iter)))
+            self.ckptios = [CheckpointIO(ospj(args.checkpoint_dir, '{:06d}_nets_ema.ckpt'.format(args.resume_iter)), **self.nets_ema)]
+
+        self.to(self.device)
+        for name, network in self.named_children():
+            # Do not initialize the FAN parameters
+            if ('ema' not in name) and ('fan' not in name):
+                print('Initializing %s...' % name)
[…]

### 2024-12-08 misc/aug/core/utils.py

@@ -1,0 +1,216 @@
+"""
+StarGAN v2
+Copyright (c) 2020-present NAVER Corp.
+
+This work is licensed under the Creative Commons Attribution-NonCommercial
+4.0 International License. To view a copy of this license, visit
+http://creativecommons.org/licenses/by-nc/4.0/ or send a letter to
+Creative Commons, PO Box 1866, Mountain View, CA 94042, USA.
+"""
+
+import os
+from os.path import join as ospj
+import json
+import glob
+from shutil import copyfile
+
+from tqdm import tqdm
+import ffmpeg
+
+import numpy as np
+import torch
+import torch.nn as nn
+import torch.nn.functional as F
+import torchvision
+import torchvision.utils as vutils
+
+
+def save_json(json_file, filename):
+    with open(filename, 'w') as f:
+        json.dump(json_file, f, indent=4, sort_keys=False)
+
+
+def print_network(network, name):
+    num_params = 0
+    for p in network.parameters():
+        num_params += p.numel()
+    # print(network)
+    print("Number of parameters of %s: %i" % (name, num_params))
+
+
+def he_init(module):
+    if isinstance(module, nn.Conv2d):
+        nn.init.kaiming_normal_(module.weight, mode='fan_in', nonlinearity='relu')
+        if module.bias is not None:
+            nn.init.constant_(module.bias, 0)
+    if isinstance(module, nn.Linear):
+        nn.init.kaiming_normal_(module.weight, mode='fan_in', nonlinearity='relu')
+        if module.bias is not None:
+            nn.init.constant_(module.bias, 0)
+
+
+def denormalize(x):
+    out = (x + 1) / 2
+    return out.clamp_(0, 1)
+
+
+def save_image(x, ncol, filename):
+    x = denormalize(x)
+    vutils.save_image(x.cpu(), filename, nrow=ncol, padding=0)
+
+
+@torch.no_grad()
+def translate_using_latent(nets, args, x_src, y_trg_list, z_trg_list, psi, filename):
+    N, C, H, W = x_src.size()
+    latent_dim = z_trg_list[0].size(1)
+    x_concat = [x_src]
+    masks = nets.fan.get_heatmap(x_src) if args.w_hpf > 0 else None
+
+    for i, y_trg in enumerate(y_trg_list):
[…]

### 2024-12-08 misc/aug/download.py

@@ -1,0 +1,3 @@
+import os
+
+os.system("git clone https://github.com/jaewoong1/SyRa-Synthesized_Rain_dataset.git")

### 2024-12-08 misc/aug/infer.py

@@ -1,0 +1,48 @@
+import torch
+from PIL import Image
+from torchvision import transforms
+import os
+from core.model import Generator
+
+# check for cuda
+device = torch.device('cuda' if torch.cuda.is_available() else 'cpu')
+print(f"Using device: {device}")
+
+# Load the model checkpoint
+checkpoint_path = '100000_nets_ema.ckpt'
+model = Generator()
+model.load_state_dict(torch.load(checkpoint_path))
+model.eval()
+
+# Define image transformation
+transform = transforms.Compose([
+    transforms.Resize((256, 256)),  # Resize to 256x256, adjust based on model input size
+    transforms.ToTensor(),  # Convert to tensor
+    transforms.Normalize((0.5, 0.5, 0.5), (0.5, 0.5, 0.5)),  # Normalization
+])
+
+# Define output directory for saving results
+output_dir = 'output_images/'
+os.makedirs(output_dir, exist_ok=True)
+
+# Process each image in the 'test/' folder
+test_dir = 'test/'
+for filename in os.listdir(test_dir):
+    if filename.endswith('.jpg'):
+        # Load and preprocess the image
+        image_path = os.path.join(test_dir, filename)
+        image = Image.open(image_path).convert('RGB')
+        image = transform(image).unsqueeze(0)  # Add batch dimension
+
+        # Run inference
+        with torch.no_grad():  # No gradient tracking during inference
+            output_image = model(image)  # Run the image through the model
+
+        # Convert output tensor back to PIL image
+        output_image = output_image.squeeze(0).cpu()  # Remove batch dimension
+        output_image = transforms.ToPILImage()(output_image)
+
+        # Save the output image
+        output_image_path = os.path.join(output_dir, f'output_{filename}')
+        output_image.save(output_image_path)
+        print(f"Processed and saved: {output_image_path}")

### 2024-12-08 misc/aug/main.py

@@ -1,0 +1,196 @@
+
+import os
+import argparse
+
+from munch import Munch
+from torch.backends import cudnn
+import torch
+
+from core.data_loader import get_train_loader
+from core.data_loader import get_test_loader
+from core.solver import Solver
+
+
+def str2bool(v):
+    return v.lower() in ('true')
+
+
+def subdirs(dname):
+    return [d for d in os.listdir(dname)
+            if os.path.isdir(os.path.join(dname, d))]
+
+
+def main(args):
+    print(args)
+    cudnn.benchmark = True
+    torch.manual_seed(args.seed)
+    #args.rain_dir = os.path.join(args.rain_dir, args.data)
+    args.out_dir = os.path.join(args.out_dir, args.data)
+    solver = Solver(args)
+
+    if args.mode == 'train':
+        assert len(subdirs(args.train_img_dir)) == args.num_domains
+        assert len(subdirs(args.val_img_dir)) == args.num_domains
+        loaders = Munch(src=get_train_loader(root=args.train_img_dir,
+                                             which='source',
+                                             img_size=args.img_size,
+                                             batch_size=args.batch_size,
+                                             prob=args.randcrop_prob,
+                                             num_workers=args.num_workers),
+                        ref=get_train_loader(root=args.train_img_dir,
+                                             which='reference',
+                                             batch_size=args.batch_size,
+                                             prob=args.randcrop_prob,
+                                             num_workers=args.num_workers),
+                        val=get_test_loader(args,
+                                            root=args.val_img_dir,
+                                            img_size=args.img_size,
+                                            batch_size=args.val_batch_size,
+                                            shuffle=True,
+                                            num_workers=args.num_workers))
+        solver.train(loaders)
+    elif args.mode == 'sample':
+        loaders = Munch(val=get_test_loader(args,
+                                            root=args.val_img_dir,
+                                            img_size=args.img_size,
+                                            batch_size=args.val_batch_size,
+                                            shuffle=False,
+                                            num_workers=args.num_workers))
+        solver.sample(loaders)
+
+    elif args.mode == 'syn':
+        loaders = Munch(val=get_test_loader(args,
+                                            root=args.rain_dir,
+                                            img_size=args.img_size,
[…]

### 2024-12-08 misc/aug/reorganize.py

@@ -1,0 +1,83 @@
+"""
+File structure of total:
+total
+-> {name}_{rest}
+
+for each file
+
+We want to restructure it so that its 
+
+test
+-> {name}
+    -> {rest}
+"""
+import os
+import shutil
+import re
+import random
+from tqdm import tqdm
+
+# List of names to match
+name_list = {
+    "art_sociology": "art_sociology_building_test",
+    "atlantic_building": "atlantic_building_test",
+    "brendan_iribe_center": "brendan_iribe_center_test",
+    "esj": "esj_building_test",
+    "farm_building": "farm_building_test",
+    "mckeldinlib": "mckeldinlib_building_test",
+    "physics_building": "physics_building_test",
+    "prince_frederick": "prince_frederick_building_test",
+    "reckord_armory": "reckord_armory_test",
+    "regents_drive": "regents_drive_parking_garage_test",
+    "yahentamitsi": "yahentamitsi_dinning_hall_test",
+    "denton": "denton_test",
+    "elkton": "elkton_test",
+    "ellicott": "ellicott_test",
+    "hagerstown": "hagerstown_test",
+    "james_clark": "james_clark_test",
+    "laplata": "laplata_test",
+    "manufacture": "manufacture_test",
+    "oakland": "oakland_test",
+    "recreation": "recreation_test",
+}
+# Directory containing all folders to be reorganized
+base_dir = 'total'
+new_base_dir = "."
+
+# Iterate over all directories in the base directory
+for folder in tqdm(os.listdir(base_dir)):
+    folder_path = os.path.join(base_dir, folder)
+    
+    # Check if it's a folder
+    if os.path.isdir(folder_path):
+        # Use regex to match the folder name with any of the names in the list
+        match = None
+        for name in name_list:
+            if re.match(f"^{name}_.+$", folder):
+                match = name
+                break
+        
+        # If a match is found, restructure the folder
+        if match:
+            dest_name = name_list[match]
+            # Extract the "rest" part of the folder name
+            rest = folder # [len(match) + 1:]  # Skip the name and underscore
+
+            # Create the new structure: 'test/{name}'
+            new_dir = f'{new_base_dir}/test/{dest_name}'
+            
+            # Create the necessary directories
+            os.makedirs(new_dir, exist_ok=True)
+
+            # choose 2 random numbers from 0,1,2,3,4
+            matches = [f'rain_{str(x)}' for x in random.sample(range(5), 2)]
+            matches += ["Clear"]
+
+            # Move contents from old folder to the new folder
[…]

### 2024-12-08 misc/slic/scripts/datasets.py

@@ -1,0 +1,132 @@
+import torch
+from torch.utils.data import DataLoader
+from torch_geometric.data import Data, Dataset 
+from torch_geometric.transforms import ToSLIC, KNNGraph
+from torch_geometric.datasets.mnist_superpixels import MNISTSuperpixels
+import os
+from torchvision import transforms
+
+from PIL import Image
+from sklearn.preprocessing import LabelEncoder
+
+class ToSLICDataset(Dataset):
+    def __init__(self, root, transform = None, slic_segments = 100, compactness=10, train = True):
+        self.classes = [
+            "art_sociology",
+            "atlantic",
+            "brendan_iribe_center",
+            "denton",
+            "elkton",
+            "ellicott",
+            "esj",
+            "farm",
+            "hagerstown",
+            "james_clark",
+            "laplata",
+            "manufacture",
+            "mckeldinlib",
+            "oakland",
+            "physics",
+            "prince_frederick",
+            "reckford_armory",
+            "recreation",
+            "regents_drive_parking_garage",
+            "yahentamitsi"
+        ]
+        self.label_encoder = LabelEncoder()
+        self.label_encoder.fit(self.classes)
+        super().__init__(root)
+        self.root = root
+        self.slic_segments = slic_segments
+        self.train = train
+        self.files = []
+        # for folder in root
+        for folder in os.listdir(root):
+            label = ""
+            # if an element of classes is in the folder name, that's the label
+            for class_ in self.classes:
+                if class_ in folder:
+                    label = self.classes.index(class_)
+            if label == "":
+                print("No label found for folder", folder)
+            for file in os.listdir(os.path.join(root, folder)):
+                self.files.append((os.path.join(root, folder, file), label))
+        self.transform = transform
+        self.to_slic = ToSLIC(slic_segments, compactness)
+    
+    def len(self):
+        return len(self.data)
+
+    def get(self, idx):
+        img_path = self.files[idx][0]
+        str_label = self.files[idx][1]
+        encoded_label = self.label_encoder.transform([str_label])[0]
+        image = Image.open(img_path).convert('RGB')
+        if self.transform:
+            image = self.transform(image)
+
+        slic = self.to_slic(image)
+        slic.y = torch.tensor([encoded_label], dtype=torch.long)
+
+        return slic
+
[…]

### 2024-12-08 misc/slic/slic.py

@@ -1,0 +1,58 @@
+import PIL.Image
+import numpy as np
+import matplotlib.pyplot as plt
+from sklearn.datasets import fetch_openml
+from skimage.segmentation import slic
+from skimage import color
+from skimage.util import img_as_float
+import cv2
+import PIL
+from torch_geometric.data import Data
+
+from utils import *
+
+# ------------------- SLIC ------------------- #
+IMAGE_DIR = './in/'
+SIZE = (224, 224)
+N_SEGMENTS = 750
+COMPACTNESS = .5
+RADIUS_FACTOR = 1/8
+MAX_NEIGHBORS = 32
+
+SCALE = 10
+EDGE_WIDTH = 5
+
+print('Loading data...')
+
+# Load images from the directory
+images = load_dir(IMAGE_DIR)  # Replace with the path to your image directory
+images = [cv2.resize(image, SIZE) for image in images]
+
+for sample_image, i in zip(images, range(len(images))):
+    slicified = slicify(sample_image, n_segments=N_SEGMENTS, compactness=COMPACTNESS, radius=SIZE[0]*RADIUS_FACTOR, max_neighbors=MAX_NEIGHBORS)
+
+    print(slicified)
+
+    slicified_image = superpixels_to_2d_image(rec=slicified, scale=SCALE, edge_width=EDGE_WIDTH, size_tuple=SIZE, bg=sample_image)
+    slicified_graph = superpixels_to_2d_image(rec=slicified, scale=SCALE, edge_width=EDGE_WIDTH, size_tuple=SIZE, bg=None)
+
+    # plot the 3 images
+    plt.figure(figsize=(15, 5))
+    plt.subplot(131)
+    plt.imshow(sample_image)
+    plt.title('Original Image')
+    plt.axis('off')
+
+    plt.subplot(132)
+    plt.imshow(slicified_image)
+    plt.title('Superpixels')
+    plt.axis('off')
+
+    plt.subplot(133)
+    plt.imshow(slicified_graph)
+    plt.title('Graph Connectivity')
+    plt.axis('off')
+
+    plt.savefig(f'./slic_{i}.png')
+
+    # plt.show()

### 2024-12-08 misc/slic/utils.py

@@ -1,0 +1,96 @@
+import torch
+import numpy as np
+import cv2
+import os
+import torchvision.transforms as T
+from torch_geometric.data import Data
+from torch_geometric.transforms import ToSLIC, RadiusGraph
+
+# Function to load images from the directory
+def load_dir(path: str) -> np.ndarray:
+    # Get all *.png, *.jpg, *.jpeg files in the directory
+    files = [f for f in os.listdir(path) if f.endswith('.png') or f.endswith('.jpg') or f.endswith('.jpeg')]
+    images = []
+    for file in files:
+        image = cv2.imread(os.path.join(path, file))
+        # Convert to RGB
+        image = cv2.cvtColor(image, cv2.COLOR_BGR2RGB)
+        images.append(image)
+    return np.array(images)
+
+# Function to convert superpixels to a 2D image using torch_geometric Data format
+def superpixels_to_2d_image(rec: Data, bg, scale: int = 30, edge_width: int = 1, size_tuple: tuple = (224,224)) -> np.ndarray:
+    # Scale the positions of the superpixels
+    rect_expand = scale * 5
+    pos = (rec.pos.clone() * scale).int()
+    new_size = (size_tuple[0] * scale, size_tuple[1] * scale)
+    # Create a blank image to display the superpixels
+    if bg is not None:
+        bg_resized = cv2.resize(bg, new_size, interpolation=cv2.INTER_LINEAR)
+        image = bg_resized.copy()
+    else:
+        image = np.full((*new_size, 3), fill_value=255, dtype=np.uint8) 
+    
+    # Draw superpixels as rectangles on the image
+    for (color, (x, y)) in zip(rec.x, pos):
+        x0, y0 = int(x), int(y)
+        x1, y1 = x0 - rect_expand//2, y0 - rect_expand//2
+        x0, y0 = x0 + rect_expand//2, y0 + rect_expand//2
+        if x1 < 0:
+            x1 = 0
+        if y1 < 0:
+            y1 = 0
+        if x0 >= new_size[0]:
+            x0 = new_size[0] - 1
+        if y0 >= new_size[1]:
+            y0 = new_size[1] - 1
+        
+        # Ensure color is a tensor with 3 elements (RGB)
+        color = color.numpy()  # Convert tensor to NumPy array
+        color = (color * 255).round().astype(np.uint8)
+        color = tuple(color.tolist())  # Convert to RGB tuple
+        # print(color, x0, y0, x1, y1)
[…]

### 2024-12-08 models/__init__.py

@@ -12,6 +12,7 @@ Models = {
     "densenet121": get_densenet121,
     "densenet161": get_densenet161,
     "densenet201": get_densenet201,
+    "vit16_224": get_vit16_224,
     # "custom": get_custom_model,  # Add your custom model here
 }
 

### 2024-12-08 models/predefined.py

@@ -1,43 +1,63 @@
 import torch.nn as nn
+import timm
 from torchvision import models
 
-def get_resnet18(num_classes=11, pretrained=False):
+def get_resnet18(num_classes=20, pretrained=False):
     resnet = models.resnet18(pretrained=pretrained)
     if num_classes != resnet.fc.out_features:
         resnet.fc = nn.Linear(resnet.fc.in_features, num_classes)
     return resnet
 
-def get_resnet34(num_classes=11, pretrained=False):
+def get_resnet34(num_classes=20, pretrained=False):
     resnet = models.resnet34(pretrained=pretrained)
     if num_classes != resnet.fc.out_features:
         resnet.fc = nn.Linear(resnet.fc.in_features, num_classes)
     return resnet
 
-def get_resnet50(num_classes=11, pretrained=False):
+def get_resnet50(num_classes=20, pretrained=False):
     resnet = models.resnet50(pretrained=pretrained)
     if num_classes != resnet.fc.out_features:
         resnet.fc = nn.Linear(resnet.fc.in_features, num_classes)
     return resnet
 
-def get_vgg11(num_classes=11):
-    return models.vgg11(num_classes=num_classes)
+def get_vgg11(num_classes=20, pretrained=False):
+    vgg = models.vgg11(pretrained=pretrained)
+    vgg.classifier[6] = nn.Linear(vgg.classifier[6].in_features, num_classes)
+    return vgg
 
-def get_vgg13(num_classes=11):
-    return models.vgg13(num_classes=num_classes)
+def get_vgg13(num_classes=20, pretrained=False):
+    vgg = models.vgg13(pretrained=pretrained)
+    vgg.classifier[6] = nn.Linear(vgg.classifier[6].in_features, num_classes)
+    return vgg
 
-def get_vgg16(num_classes=11):
-    return models.vgg16_bn(num_classes=num_classes)
+def get_vgg16(num_classes=20, pretrained=False):
+    vgg = models.vgg16_bn(pretrained=pretrained)
+    vgg.classifier[6] = nn.Linear(vgg.classifier[6].in_features, num_classes)
+    return vgg
 
-def get_vgg19(num_classes=11):
-    return models.vgg19(num_classes=num_classes)
+def get_vgg19(num_classes=20, pretrained=False):
+    vgg = models.vgg19(pretrained=pretrained)
+    vgg.classifier[6] = nn.Linear(vgg.classifier[6].in_features, num_classes)
[…]

### 2024-12-08 old_code/cam.py

@@ -1,0 +1,114 @@
+import numpy as np
+import torch
+import cv2
+import warnings
+# Suppress FutureWarnings
+warnings.filterwarnings("ignore", category=FutureWarning, message="Using a non-full backward hook when the forward contains multiple autograd Nodes is deprecated")
+
+#This is for visualizing the 
+#If you find this code not good, fix it please. Appriciated.
+
+class GradCAM:
+    def __init__(self, model, target_layer):
+        self.model = model
+        self.target_layer = target_layer
+        self.gradients = None
+        self.hook()
+
+    def hook(self):
+        def forward_hook(module, input, output):
+            self.features = output
+
+        def backward_hook(module, grad_in, grad_out):
+            self.gradients = grad_out[0]
+
+        target_layer = dict(self.model.named_modules())[self.target_layer]
+        target_layer.register_forward_hook(forward_hook)
+        target_layer.register_backward_hook(backward_hook)
+
+    def generate(self, input_tensor, target_class):
+        model_output = self.model(input_tensor)
+        self.model.zero_grad()
+
+        one_hot_output = torch.zeros((1, model_output.size()[-1])).to(device)
+        one_hot_output[0][target_class] = 1
+        model_output.backward(gradient=one_hot_output)
+
+        grad = self.gradients.data.cpu().numpy()[0]
+        features = self.features.data.cpu().numpy()[0]
+        weights = np.mean(grad, axis=(1, 2))
+
+        # generate cam
+        cam = np.zeros(features.shape[1:], dtype=np.float32)
+
+        for i, w in enumerate(weights):
+            cam += w * features[i]
+
+        cam = np.maximum(cam, 0)
+
+        # Normalize the CAM
+        cam = cam - np.min(cam)  # Shift the values to make the minimum zero
+        eps = 1e-7  # Small value to prevent division by zero
+        cam = cam / (np.max(cam) + eps)  # Normalize the CAM
+        cam = np.nan_to_num(cam)  # Replace NaNs with zeros if any
+
+        # Resize CAM to match the input image size
+        cam = cv2.resize(cam, (448, 448))
+
+        return cam
+    
+
+class GradCAMPlusPlus:
+    def __init__(self, model, target_layer):
+        self.model = model
+        self.target_layer = target_layer
+        self.gradients = None
+        self.activations = None
+        self.hook()
+
+    def hook(self):
+        def forward_hook(module, input, output):
[…]

### 2024-12-08 slic/scripts/datasets.py

@@ -1,132 +1,0 @@
-import torch
-from torch.utils.data import DataLoader
-from torch_geometric.data import Data, Dataset 
-from torch_geometric.transforms import ToSLIC, KNNGraph
-from torch_geometric.datasets.mnist_superpixels import MNISTSuperpixels
-import os
-from torchvision import transforms
-
-from PIL import Image
-from sklearn.preprocessing import LabelEncoder
-
-class ToSLICDataset(Dataset):
-    def __init__(self, root, transform = None, slic_segments = 100, compactness=10, train = True):
-        self.classes = [
-            "art_sociology",
-            "atlantic",
-            "brendan_iribe_center",
-            "denton",
-            "elkton",
-            "ellicott",
-            "esj",
-            "farm",
-            "hagerstown",
-            "james_clark",
-            "laplata",
-            "manufacture",
-            "mckeldinlib",
-            "oakland",
-            "physics",
-            "prince_frederick",
-            "reckford_armory",
-            "recreation",
-            "regents_drive_parking_garage",
-            "yahentamitsi"
-        ]
-        self.label_encoder = LabelEncoder()
-        self.label_encoder.fit(self.classes)
-        super().__init__(root)
-        self.root = root
-        self.slic_segments = slic_segments
-        self.train = train
-        self.files = []
-        # for folder in root
-        for folder in os.listdir(root):
-            label = ""
-            # if an element of classes is in the folder name, that's the label
-            for class_ in self.classes:
-                if class_ in folder:
-                    label = self.classes.index(class_)
-            if label == "":
-                print("No label found for folder", folder)
-            for file in os.listdir(os.path.join(root, folder)):
-                self.files.append((os.path.join(root, folder, file), label))
-        self.transform = transform
-        self.to_slic = ToSLIC(slic_segments, compactness)
-    
-    def len(self):
-        return len(self.data)
-
-    def get(self, idx):
-        img_path = self.files[idx][0]
-        str_label = self.files[idx][1]
-        encoded_label = self.label_encoder.transform([str_label])[0]
-        image = Image.open(img_path).convert('RGB')
-        if self.transform:
-            image = self.transform(image)
-
-        slic = self.to_slic(image)
-        slic.y = torch.tensor([encoded_label], dtype=torch.long)
-
-        return slic
-
[…]

### 2024-12-08 slic/scripts/model.py

@@ -1,63 +1,0 @@
-import torch
-from torch import nn
-from torch_geometric.nn import GATConv
-
-
-class GNNImageClassificator(nn.Module):
-    """
-    See Figure 2 from https://iopscience.iop.org/article/10.1088/1742-6596/1871/1/012071/pdf
-    """
-    def __init__(
-        self,
-        in_channels: int = 3,
-        hidden_dim: int = 152,
-        num_classes: int = 10,
-    ):
-        super().__init__()
-
-        self.in_channels = in_channels
-        self.hidden_dim = hidden_dim
-        self.num_classes = num_classes
-
-        self.conv1 = GATConv(in_channels=in_channels, out_channels=hidden_dim)
-        self.conv2 = GATConv(in_channels=hidden_dim, out_channels=hidden_dim)
-        self.conv3 = GATConv(in_channels=in_channels + hidden_dim, out_channels=hidden_dim)
-
-        self.fc = nn.Sequential(
-            nn.Linear(in_channels + 3 * hidden_dim, 256),
-            nn.ReLU(True),
-            nn.Linear(256, 32),
-            nn.ReLU(True),
-            nn.Linear(32, 32),
-            nn.ReLU(True),
-            nn.Linear(32, num_classes),
-        )
-
-    def forward_one_base(self, node_features: torch.Tensor, edge_indices: torch.Tensor) -> torch.Tensor:
-        assert node_features.ndim == 2 and node_features.shape[1] == self.in_channels
-        assert edge_indices.ndim == 2 and edge_indices.shape[0] == 2
-
-        x0 = node_features
-
-        x1 = self.conv1(x0, edge_indices)
-
-        x2 = self.conv2(x1, edge_indices)
-        x0_x2 = torch.cat((x0, x2), dim=-1)
-
-        x3 = self.conv3(x0_x2, edge_indices)
-        x0_x1_x2_x3 = torch.cat((x0, x1, x2, x3), dim=-1)
-
-        return x0_x1_x2_x3
-
-    def forward(self, batch_node_features: list[torch.Tensor], batch_edge_indices: list[torch.Tensor]) -> torch.Tensor:
-        assert len(batch_node_features) == len(batch_edge_indices)
-
-        features_list = []
-        for node_features, edge_indices in zip(batch_node_features, batch_edge_indices):
-            features_list.append(self.forward_one_base(node_features=node_features, edge_indices=edge_indices))
-
[…]

### 2024-12-08 slic/scripts/train.py

@@ -1,126 +1,0 @@
-from typing import Callable, cast
-
-import click
-import torch
-import wandb
-from torch.utils.data import DataLoader
-
-from gnn_image_classification.datasets import build_train_val_dataloaders
-from gnn_image_classification.model import GNNImageClassificator
-
-
-def train_one_epoch(
-    model: GNNImageClassificator,
-    optimizer: torch.optim.Optimizer,
-    train_loader: DataLoader,
-    criterion: Callable,
-    batches_passed: int,
-) -> int:
-    model.train()
-    for batch in train_loader:
-        batch_node_features = batch["batch_node_features"]
-        batch_edge_indices = batch["batch_edge_indices"]
-        classes = batch["classes"]
-
-        logits = model(batch_node_features=batch_node_features, batch_edge_indices=batch_edge_indices)
-        predicted_classes = torch.argmax(logits, dim=1)
-
-        loss = criterion(logits, classes).mean()
-
-        optimizer.zero_grad()
-        loss.backward()
-        optimizer.step()
-
-        accuracy = (predicted_classes == classes).to(torch.float32).mean()
-
-        wandb.log({
-            "train_accuracy": float(accuracy.detach().cpu().numpy()),
-            "train_loss": float(loss.detach().cpu().numpy()),
-            "batch": batches_passed,
-        })
-
-        batches_passed += 1
-
-    return batches_passed
-
-
-@torch.no_grad()
-def evaluate(
-    model: GNNImageClassificator,
-    val_loader: DataLoader,
-    epochs_passed: int,
-) -> None:
-    model.eval()
-
-    accuracy_sum: float = 0.0
-    num_samples: int = 0
-
-    for batch in val_loader:
-        batch_node_features = batch["batch_node_features"]
-        batch_edge_indices = batch["batch_edge_indices"]
-        classes = batch["classes"]
-
-        logits = model(batch_node_features=batch_node_features, batch_edge_indices=batch_edge_indices)
-        predicted_classes = torch.argmax(logits, dim=1)
-
-        accuracy_sum += float((predicted_classes == classes).to(torch.float32).mean().cpu().numpy()) * len(classes)
-        num_samples += len(classes)
-
-    accuracy = accuracy_sum / num_samples
-
-    wandb.log({
-        "val_accuracy": accuracy,
-        "epoch": epochs_passed,
-    })
-
-
-@click.command()
-@click.option("--batch-size", type=int, default=64)
[…]

### 2024-12-08 slic/slic.py

@@ -1,58 +1,0 @@
-import PIL.Image
-import numpy as np
-import matplotlib.pyplot as plt
-from sklearn.datasets import fetch_openml
-from skimage.segmentation import slic
-from skimage import color
-from skimage.util import img_as_float
-import cv2
-import PIL
-from torch_geometric.data import Data
-
-from utils import *
-
-# ------------------- SLIC ------------------- #
-IMAGE_DIR = './in/'
-SIZE = (224, 224)
-N_SEGMENTS = 750
-COMPACTNESS = .5
-RADIUS_FACTOR = 1/8
-MAX_NEIGHBORS = 32
-
-SCALE = 10
-EDGE_WIDTH = 5
-
-print('Loading data...')
-
-# Load images from the directory
-images = load_dir(IMAGE_DIR)  # Replace with the path to your image directory
-images = [cv2.resize(image, SIZE) for image in images]
-
-for sample_image, i in zip(images, range(len(images))):
-    slicified = slicify(sample_image, n_segments=N_SEGMENTS, compactness=COMPACTNESS, radius=SIZE[0]*RADIUS_FACTOR, max_neighbors=MAX_NEIGHBORS)
-
-    print(slicified)
-
-    slicified_image = superpixels_to_2d_image(rec=slicified, scale=SCALE, edge_width=EDGE_WIDTH, size_tuple=SIZE, bg=sample_image)
-    slicified_graph = superpixels_to_2d_image(rec=slicified, scale=SCALE, edge_width=EDGE_WIDTH, size_tuple=SIZE, bg=None)
-
-    # plot the 3 images
-    plt.figure(figsize=(15, 5))
-    plt.subplot(131)
-    plt.imshow(sample_image)
-    plt.title('Original Image')
-    plt.axis('off')
-
-    plt.subplot(132)
-    plt.imshow(slicified_image)
-    plt.title('Superpixels')
-    plt.axis('off')
-
-    plt.subplot(133)
-    plt.imshow(slicified_graph)
-    plt.title('Graph Connectivity')
-    plt.axis('off')
-
-    plt.savefig(f'./slic_{i}.png')
-
-    # plt.show()

### 2024-12-08 slic/utils.py

@@ -1,96 +1,0 @@
-import torch
-import numpy as np
-import cv2
-import os
-import torchvision.transforms as T
-from torch_geometric.data import Data
-from torch_geometric.transforms import ToSLIC, RadiusGraph
-
-# Function to load images from the directory
-def load_dir(path: str) -> np.ndarray:
-    # Get all *.png, *.jpg, *.jpeg files in the directory
-    files = [f for f in os.listdir(path) if f.endswith('.png') or f.endswith('.jpg') or f.endswith('.jpeg')]
-    images = []
-    for file in files:
-        image = cv2.imread(os.path.join(path, file))
-        # Convert to RGB
-        image = cv2.cvtColor(image, cv2.COLOR_BGR2RGB)
-        images.append(image)
-    return np.array(images)
-
-# Function to convert superpixels to a 2D image using torch_geometric Data format
-def superpixels_to_2d_image(rec: Data, bg, scale: int = 30, edge_width: int = 1, size_tuple: tuple = (224,224)) -> np.ndarray:
-    # Scale the positions of the superpixels
-    rect_expand = scale * 5
-    pos = (rec.pos.clone() * scale).int()
-    new_size = (size_tuple[0] * scale, size_tuple[1] * scale)
-    # Create a blank image to display the superpixels
-    if bg is not None:
-        bg_resized = cv2.resize(bg, new_size, interpolation=cv2.INTER_LINEAR)
-        image = bg_resized.copy()
-    else:
-        image = np.full((*new_size, 3), fill_value=255, dtype=np.uint8) 
-    
-    # Draw superpixels as rectangles on the image
-    for (color, (x, y)) in zip(rec.x, pos):
-        x0, y0 = int(x), int(y)
-        x1, y1 = x0 - rect_expand//2, y0 - rect_expand//2
-        x0, y0 = x0 + rect_expand//2, y0 + rect_expand//2
-        if x1 < 0:
-            x1 = 0
-        if y1 < 0:
-            y1 = 0
-        if x0 >= new_size[0]:
-            x0 = new_size[0] - 1
-        if y0 >= new_size[1]:
-            y0 = new_size[1] - 1
-        
-        # Ensure color is a tensor with 3 elements (RGB)
-        color = color.numpy()  # Convert tensor to NumPy array
-        color = (color * 255).round().astype(np.uint8)
-        color = tuple(color.tolist())  # Convert to RGB tuple
-        # print(color, x0, y0, x1, y1)
[…]

### 2024-12-08 train.py

@@ -1,233 +1,0 @@
-import argparse
-import os
-import torch
-import torch.nn as nn
-import torch.optim as optim
-import matplotlib.pyplot as plt
-import numpy as np
-import cv2
-
-from cam import *
-from models import get_model #our models 
-from dataset import LabeledDataset
-from torch.utils.data import DataLoader
-from torchvision import transforms
-from tqdm import tqdm # for progress bar stuff
-
-# If you don't like the layout of the code, fix it. Appriciated :)
-
-#TODO: If the code is wrong, fix it
-
-class Config: #TODO: might change something here
-    DEVICE = torch.device("cuda" if torch.cuda.is_available() else "cpu")
-    MODEL_NAME = "resnet18"
-    EPOCHS = 10
-    LR = 0.001
-    BATCH_SIZE = 32
-    CLASS_KEYWORDS = [
-    "art_sociology",
-    "atlantic",
-    "brendan_iribe",
-    "esj",
-    "farm",
-    "mckeldinlib",
-    "physics",
-    "prince_frederick",
-    "reckord_armory",
-    "regents_drive",
-    "yahentamitsi_dinning"]
-
-def train_with_metrics(model, 
-                       train_loader, 
-                       val_loader, 
-                       test_loader, 
-                       criterion, 
-                       optimizer, 
-                       config, 
-                       checkpoint_path="checkpoint.pth"):
-    
-    metrics = {"train_acc": [], "val_acc": []}
-    best_val_acc = 0.0
-    start_epoch = 0
-
-    # Check if checkpoint exists
-    if os.path.exists(checkpoint_path):
-        print(f"Resuming from checkpoint: {checkpoint_path}")
-        checkpoint = torch.load(checkpoint_path)
-        model.load_state_dict(checkpoint['model_state'])
-        optimizer.load_state_dict(checkpoint['optimizer_state'])
-        start_epoch = checkpoint['epoch'] + 1
-        metrics = checkpoint['metrics']
-        best_val_acc = checkpoint['best_val_acc']
-
-    # Training epoch starts here...
-    for epoch in range(start_epoch, config.EPOCHS):
-        model.train()
-        train_loss, correct, total = 0.0, 0, 0
-
-        # Training phase
-        for images, labels in tqdm(train_loader, desc=f"Epoch {epoch+1}/{config.EPOCHS} [Training]"):
[…]

### 2024-12-08 report/paper/draft.tex
paper to local

@@
 \begin{itemize}
-    \item On the topic of image recognition/classification, AlexNet, VGG, and Resnet are strong examples of traditional CNN recognition and classification models.
-We intend to build on their techniques.
-    \item With respect to image segmentation, we may end up using Grad-CAM/Score-CAM as detailed after this section.
-However, we will compare with traditional segmentation techniques as detailed in class (proposals and culling, and we can implement something similar to U-Net)
+    \item On the topic of image recognition/classification, AlexNet, VGG, and Resnet are strong examples of fully supervised traditional CNN recognition and classification models. 
+    \item With respect to image segmentation, we end up using Grad-CAM/Score-CAM as detailed after this section.
 \end{itemize}
@@
 
+We prioritized utilizing Semi-Supervised Methods of image recognition. For this, we used FixMatch and MeanTeach methods.
+
 % Write: how gradcam can help find the location of the building in the image (to help find its not on the foreground images), point out how this isn't the case in prelim
@@
 \begin{itemize} % IP: Gradcam, Scorecam, Gradcam++
-    \item Grad-CAM, Selvaraju, et al.\ (2019), uses the final gradient into the last convolution layer to produce a visual representation of strength in decision making.
+    \item \citet{selvaraju} Grad-CAM, Selvaraju, et al.\ (2019), uses the final gradient into the last convolution layer to produce a visual representation of strength in decision making.
 This is a visual indicator of model strength and is on paper highly useful for highlighting image classification confidence, but can also be used to help define segmentation.
@@
 
+% https://www.getbibtex.com
+
 \end{document}

### 2024-12-08 report/paper/draft.tex
background

@@
 % before loading neurips_2024
-
-% ready for submission
-\usepackage[final]{neurips_2024}
+\PassOptionsToPackage{numbers, compress}{natbib}
 
@@
 % to avoid loading the natbib package, add option nonatbib:
-%    \usepackage[nonatbib]{neurips_2024}
+\usepackage[final]{neurips_2024}
 
@@
 
-\title{ UMD Building Classification Proposal }
+\title{ UMD Building Classification }
 
@@
 
-The primary motivator for this project lies in the challenge of combined segmentation of multiple buildings in an image and the subsequent classification of them, while also segmenting and accounting for foreground blocking objects (eg.
-pedestrians, trees, cars).
-While from a purely practical standpoint it's true that buildings are mapped (eg.
-Google Maps) already, this still represents a strong "AR-like" result.
+Although not addressing an urgent problem, our goal was to gain experience with the entire deep learning lifecycle, from data acquisition to final model evaluation.
+We built our own image database from scratch and conducted extensive experiments with a variety of supervised and semi-supervised learning models to ensure the highest accuracy.
+
+The challenge came from the fact that we had to build our own dataset from scratch.
+We additionally worked with implementation of high resolution images on limited datasets to semi-supervised methods, along with the use of Grad-CAM and Score-CAM for image segmentation.
+
+We additionally did experiments on GNNs and HITL with Grad-CAM.
 
@@
 \begin{itemize}
-    \item On the topic of image recognition/classification, AlexNet, VGG, and Resnet are strong examples of fully supervised traditional CNN recognition and classification models. 
+    \item On the topic of image recognition/classification, AlexNet, VGG, and Resnet\cite{krizhevsky}\cite{simonyan}\cite{he} are strong examples of fully supervised traditional CNN recognition and classification models.
     \item With respect to image segmentation, we end up using Grad-CAM/Score-CAM as detailed after this section.
@@
 
-This also includes significant work being done on visual explanations of CNN models via Selvaraju, et al.\ (2019) Grad-CAM and other related works.
+This also includes significant work being done on visual explanations of CNN models via Selvaraju, et al.\cite{selvaraju} (2019) Grad-CAM and other related works.
 These can be used as an alternative method of segmentation and recognition.
@@
 
+\begin{itemize}
+    \item FixMatch, Sohn, et al.\cite{sohn} (2020), is a semi-supervised learning method that generates “pseudo-labels” using model predictions on weakly augmented unlabeled data, retained only if it’s high confidence; then, train to predict that pseudo label with a strongly augmented version.
+
+    This is a strong method for semi-supervised learning with limited datasets, so will be one of our main driving methods of implementation.
+    \item MeanTeacher, Tarvainen, et al.\cite{tarvainen} (2017), is a semi-supervised learning method that uses a teacher model to provide a consistent target for the student model.
+The teacher model is an exponential moving average of the student model, and the student model is trained to match the teacher model’s predictions.
+
+    At each training step, introduce the same minibatch with random augmentation to separate them. Note that this requires noise in the model.
+
+    This method can be used to improve the performance of the model, especially when the dataset is relatively small, as in ours
+\end{itemize}
+
 % Write: how gradcam can help find the location of the building in the image (to help find its not on the foreground images), point out how this isn't the case in prelim
@@
 \begin{itemize} % IP: Gradcam, Scorecam, Gradcam++
-    \item \citet{selvaraju} Grad-CAM, Selvaraju, et al.\ (2019), uses the final gradient into the last convolution layer to produce a visual representation of strength in decision making.
+    \item Grad-CAM, Selvaraju, et al.\cite{selvaraju} (2019), uses the final gradient into the last convolution layer to produce a visual representation of strength in decision making.
 This is a visual indicator of model strength and is on paper highly useful for highlighting image classification confidence, but can also be used to help define segmentation.
     % https://arxiv.org/abs/1610.02391 gradcam
-    \item Grad-CAM++, Chattopadhay, et al.\ (2018) is an upgrade to Grad-CAM by generalizing it.
+    \item Grad-CAM++, Chattopadhay, et al.\cite{chattopadhay} (2018) is an upgrade to Grad-CAM by generalizing it.
 It can then isolate/identify multiple object instances in a single image (important for our proposal due to the presence of multiple buildings in images) and a generally improved visual indicator.
     % https://arxiv.org/abs/1710.11063 gradcam++
-    \item Score-CAM, Wang, et al.\ (2020) is an alternative approach to Grad-CAM that completely discards using the gradient and instead evaluates the weight of each activation map in the forward pass.
+    \item Score-CAM, Wang, et al.\cite{wang} (2020) is an alternative approach to Grad-CAM that completely discards using the gradient and instead evaluates the weight of each activation map in the forward pass.
     % https://arxiv.org/abs/1910.01279 scorecam
@@
 
-\begin{figure}
+\begin{figure}[h]
     \centering
     \includegraphics[width=0.3\linewidth]{fig1.png}
-    \caption{Preliminary Grad-CAM results}
+    \caption{Preliminary Grad-CAM results example}
     \label{fig:prelim_results_1}
@@
 
-\subsection{Motivation for Proposed Methods}
+We additionally used GNN methods and HITL methods. \begin{itemize}
+    \item Graph Neural Networks are a method of using graph data to make predictions.
+This can be used to make predictions on the labeled/unlabeled samples as nodes, and should this perform reasonably this can be used as a primary paradigm as well.
+
+    The main motivator for this is that nodes can be connected by edges to represent relationships that go beyond stride.
+
+    Long et al.\cite{long} (2020) is prior work on GNN image recognition, done on the MNIST dataset on low resolution black and white images.
+Our intention is to innovate by extending this to high resolution color images of buildings.
+
+    \item Superpixels are a method of dividing an image into regions of similar color.
+This can be used to help segment the image and can be used to help the model focus on the building itself.
+This is a method of image segmentation that can be used to help the model focus on the building itself.
+For graphs, this is a method of reducing the complexity greatly.
+
+    The SLIC-Superpixel transform, developed by EPFL labs \cite{epflSLICSuperpixels}, is a strong method of superpixel generation that can be used to help segment the image.
+This can be used to focus node complexity on details.
+    \item HITL is human corrections on the network to help the network focus on areas of interest by providing absolute feedback on whether or not Grad-CAM is focusing on the correct areas.
+\end{itemize}
+
+\subsection{Motivation for Methods}
 
@@
 
-\section{Proposed Approach}
+The focus is to see if we can get Grad-CAM to focus on the elements of the image that are important, to help "guide" the model to focus on the building itself.
+This is important because the model may be making predictions based on unrelated objects in the image, and this can be used to confirm model confidence.
+
+\section{Approach}
 \label{approach}
@@
 
-\section*{References}
-\label{cites}
-
 \medskip
 
-{
 \small
 
-% Cite format MLA 9 - Jeffery
-[1] Krizhevsky, Alex, et al.
-“ImageNet Classification with Deep Convolutional Neural Networks.” Communications of the ACM, vol.
-60, no.
-6, May 2012, pp.
-84–90, proceedings.neurips.cc/paper\_files/paper/2012/file/c399862d3b9d6b76c8436e924a68c45b-Paper.pdf.
-
-[2] Simonyan, Karen, and Andrew Zisserman. “Very Deep Convolutional Networks for Large-Scale Image Recognition.” ArXiv.org, 10 Apr. 2015, arxiv.org/abs/1409.1556.
-
-[3] He, Kaiming, et al. “Deep Residual Learning for Image Recognition.” ArXiv.org, arXiv, 10 Dec. 2015, arxiv.org/abs/1512.03385.
-
-[4] Selvaraju, Ramprasaath R., et al.
-“Grad-CAM: Visual Explanations from Deep Networks via Gradient-Based Localization.” International Journal of Computer Vision, vol.
-128, no.
-2, Feb.
-2020, pp.
-336–59, https://doi.org/10.1007/s11263-019-01228-7.
-
-[5] Chattopadhay, Aditya, et al.
-“Grad-CAM++: Generalized Gradient-Based Visual Explanations for Deep Convolutional Networks.” 2018 IEEE Winter Conference on Applications of Computer Vision (WACV), Mar.
-2018, https://doi.org/10.1109/wacv.2018.00097.
-
-[6] Wang, Haofan, et al. “Score-CAM: Score-Weighted Visual Explanations for Convolutional Neural Networks.” ArXiv:1910.01279 [Cs], Apr. 2020, arxiv.org/abs/1910.01279.
+\bibliographystyle{abbrv}
+\bibliography{sources}
 

### 2024-12-08 report/paper/draft.tex
3 pages of 6 done, formatting and headers for now

@@
 
-    The SLIC-Superpixel transform, developed by EPFL labs \cite{epflSLICSuperpixels}, is a strong method of superpixel generation that can be used to help segment the image.
+    The SLIC-Superpixel transform, developed by EPFL labs \cite{epflSLICSuperpixels}, is a method of superpixel generation that can be used to help segment the image.
 This can be used to focus node complexity on details.
@@
 
-\section{Approach}
-\label{approach}
+\section{Methods}
+\label{method}
 
@@
 
-All data will be collected by group members individually.
-We plan to select a set of UMD buildings (at least 10-15) for the classification.
-Each building will have at least 50 images taken using our phones from different angles, distances, and lighting (eg.
-time of day).
-We plan to do data augmentation for the buildings.
+Data was collected by individually taking pictures and labeling them, along with data augmentation.
+We took around 4000 photos of UMD buildings over 20 classes, aiming for a 60/40 split of daytime/nighttime photos.
 
-Preprocessing will be done to normalize/resize images to a standard, strip metadata, and we will also consider color segmenting the building out of the image (eg.
-filtering out possible noise from the sky/foreground, although this will have the detriment of making it less robust).
-We also consider using alternative encodings; HSV may help given the UMD red-brown brick style
+Care was taken to ensure that the photos were taken from a variety of angles and distances. We were limited in time and season since data collection occurred mainly over the course of 2 weeks in fall.
 
-Should the dataset be large, it can be proposed to train multiple models and utilize model averaging/ensemble voting to merge.
+The dataset was split 80/10/10 for training/validation/testing. Photos were augmented by displacement and inherently varied by rotation. All images were resized to 224x224 for training.
 
-\subsection{Paradigm}
+Test images were further augmented by adding noise and other transforms, including the SyRA synthesized rain (Choi et al. \cite{choi}) method to add rain streaks to the images.
 
-We intend to use a CNN architecture, loosely based around existing methods, in a semi-supervised format. We can use MeanTeacher or FixMatch for the method of semi-supervised learning.
+\subsection{Fully Supervised Baseline}
 
-It's also possible to use a graph based method and a GNN.
-It would be interesting to attempt this by using labeled/unlabled samples as nodes, and should this perform reasonably this can be used as a primary paradigm as well.
+A fully supervised model was implemented using various ResNet/VGG models for the sake of both comparison and as a baseline for our semi-supervised methods.
+After training ResNet18 was determined to be best with a 97\% accuracy on test set after %%TODO: fill in
 
-Training can be done on Google Colab, but we also have the option of using a training server (SAIL @ Columbia)
+\subsection{Semi-Supervised Methods}
 
-\section{Expected Plan}
-\label{plan}
+\subsubsection{Grad-CAM/Score-CAM}
 
-\subsection{Timeline}
+\subsubsection{Fixmatch}
 
-\begin{enumerate}
-    \item Nov 1 - We intend to have the dataset ready. At the time of writing we have \verb|~|1k photos before augmentation and processing.
-    \item Mid Nov - We want to ensure we have image classification trained correctly on building recognition for simple cases (single buildings with noise and on various conditions). 
-    \item End Nov - Hyper parameter tuning/Grad-CAM++/Score-CAM visualizations to improve the performance of the CNN architecture.
-Ensure via Grad-CAM that the model is confident and attempt preliminary segmentation on multiple instances and find confidence.
-    \item December - Utilize alternative segmentation methods (Grad-CAM/Score-CAM lineage) and alternative architecture (GNNs) and compare with our results.
-\end{enumerate}
+\subsubsection{MeanTeacher}
 
-Note - preliminary results indicate that Score-CAM may be too slow to be ideal on our set.
+\subsection{GNNs/HITL/VQA Experiments}
 
-% chronological plans
+% results for these will go into appendix
 
-\subsection{Moonshot Goals}
+\subsubsection{GNNs}
 
-% Show a 3D version of the UMD building given by a 2D image as input.
-% Take all images of all UMD buildings, including the building interiors, for classification.
-% Based on our database of images, generate an image that represents UMD building styles using diffusion models.
-% video?\
+\subsubsection{HITL}
 
-We have a variety of higher level goals for our project beyond just the basic plan. \begin{itemize}
-    \item First, should our model performance be tuned to be sufficiently fast, we would like to be able to apply it to videos.
-Sampling a video at 5-10 fps and passing it through the video is a simple way to accomplish this given enough performance.
-    \item Being able to classify all buildings on UMD (there are a lot of them) rather than just those in the central dataset. 
-    \item Being able to identify architectural styles beyond just building names.
-If the model is sufficiently confident we could even write a model to generate representative images of UMD architecture using a diffusion model (a long shot because it requires massive architecture changes)
-    \item Reconstruct a 3-D model of the building using a 2-D model as input (eg.
-not just classification but an understanding of what the building actually looks like - this is a long shot because it would likely require a lot of data and huge paradigm changes)
-    \item Interior identification of buildings (much harder due to a potential lack of distinguishing features)
-\end{itemize}
+\subsubsection{VQA}
+
+\section{Results}
+\label{result}
+
+\subsection{Code}
+
+Code for models, data collection and augmentation, along with the SLIC methods and HITL methods, were written and implemented in pytorch and can be found on our Github repository: \url{https://github.com/BlueTurtle123/CMSC472_Final_Project}
+
+\subsection{Fully Supervised Baseline}
+
+% Demonstrate stats
+
+\subsection{Semi-Supervised Methods}
+
+% Demonstrate stats
+
+\subsection{Other Experiments}
+
+\subsubsection{HITL}
+
+\subsubsection{GNN SLIC Transform}
+
+% quick overview of new transform and then note results in appendix
+
+\subsubsection{VQA}
+
+% quick overview of VQA and then note results in appendix
 

### 2024-12-09 report/paper/draft.tex
for now

@@
 
+\usepackage{graphicx} % Required for inserting images
+\usepackage{tikz}
+\usepackage{soul}
+\usepackage{amsmath}
+\usepackage{listings}
+\usepackage{amssymb}
+\usepackage{float}
+\usepackage{parskip}
+\usepackage{pgfplots}
+\usepackage{xcolor}
+\usepackage[shortlabels]{enumitem}
+
+\newcommand*{\Perm}[2]{{}^{#1}\!P_{#2}}%
+\newcommand*{\Comb}[2]{{}^{#1}C_{#2}}%
+\newcommand*{\qed}{\hfill$\square$}%
+\newcommand*{\txt}[1]{\text{ #1 }}%
+\newcommand*{\iprod}[1]{\langle #1 \rangle}
+\newcommand*{\fora}{\txt{}\forall}%
+\newcommand*{\rr}{\mathbb{R}}%
+
 \title{ UMD Building Classification }
@@
 \author{%
+  Jerry Li\\
+  \texttt{jli103@umd.edu} \\
+  \And 
   Can Li \\
@@
   \texttt{jtian12@umd.edu} \\
-  \And 
-  Jerry Li\\
-  \texttt{jli103@umd.edu} \\
   \And 
@@
 
+%% TODO: 
+%% Can's notes on data collection, FixMatch
+%% https://arxiv.org/pdf/1412.6856
+%% http://cnnlocalization.csail.mit.edu/Zhou_Learning_Deep_Features_CVPR_2016_paper.pdf
+%% https://arxiv.org/pdf/1610.02391
+%% https://github.com/kekmodel/FixMatch-pytorch
+%% https://link.springer.com/article/10.1007/s10462-022-10246-w
+%%
+
 \begin{abstract}
-  We propose that, given an input image of a UMD building, we can classify the building with the correct name in close to realtime using CNN image segmentation and classification methods.
-What makes this project valuable for educational purposes is that we will explore how to build our image database from scratch, experiment with different convolution neural networks, different ways to visualize the CNN layers for debugging our network design and potentially even for segmentation, and utilizing semi-supervised learning.
+    With the rise of new computational architectures for image processing and classification, computer vision systems are highly diverse, raising the question of which approach is the most effective for a given task.
+Our study focuses on designing and evaluating a reliable classification system for identifying buildings on the University of Maryland campus using semi-supervised CNN.
+By constructing a custom image database from scratch and experimenting with various architectures for semi-supervised learning, we aim to identify the best model for our classification problem.
+Additionally, we utilize CNN visualization eg.
+Grad-CAM to further assess our model’s performance.
 \end{abstract}
@@
 The challenge came from the fact that we had to build our own dataset from scratch.
-We additionally worked with implementation of high resolution images on limited datasets to semi-supervised methods, along with the use of Grad-CAM and Score-CAM for image segmentation.
+We additionally worked with implementation of high resolution images on limited datasets to semi-supervised methods, along with the use of Grad-CAM for image segmentation.
 
@@
     \item On the topic of image recognition/classification, AlexNet, VGG, and Resnet\cite{krizhevsky}\cite{simonyan}\cite{he} are strong examples of fully supervised traditional CNN recognition and classification models.
-    \item With respect to image segmentation, we end up using Grad-CAM/Score-CAM as detailed after this section.
+    \item With respect to image segmentation, we end up using Grad-CAM as detailed after this section.
 \end{itemize}
@@
 The teacher model is an exponential moving average of the student model, and the student model is trained to match the teacher model’s predictions.
-
-    At each training step, introduce the same minibatch with random augmentation to separate them. Note that this requires noise in the model.
-
-    This method can be used to improve the performance of the model, especially when the dataset is relatively small, as in ours
 \end{itemize}
@@
     % https://arxiv.org/abs/1710.11063 gradcam++
-    \item Score-CAM, Wang, et al.\cite{wang} (2020) is an alternative approach to Grad-CAM that completely discards using the gradient and instead evaluates the weight of each activation map in the forward pass.
-    % https://arxiv.org/abs/1910.01279 scorecam
 \end{itemize}
 
-Grad-CAM++ and Score-CAM can both be used as an important means for highlighting image classification confidence, both of which we intend to use as the most advanced methods in their respective lineages.
+Grad-CAM++ can be used as an important means for highlighting image classification confidence, both of which we intend to use as the most advanced methods in their respective lineages.
 As an example, see our preliminary original Grad-CAM results in Figure 1 on instances on our test set, where Grad-CAM indicates it's making predictions based on unrelated objects (foreground foliage, people, unrelated elements of the building).
@@
 If the model is sufficiently confident, this can even be used as a means to indicate building locations (especially given Grad-CAM++ ability to find multiple instances) within the image rather than using traditional segmentation techniques.
-
-Figure 2 (attached to the appendix) has examples utilizing Grad-CAM++ on architecture similar to ResNet.
-
-\begin{figure}[h]
-    \centering
-    \includegraphics[width=0.3\linewidth]{fig1.png}
-    \caption{Preliminary Grad-CAM results example}
-    \label{fig:prelim_results_1}
-\end{figure}
 
@@
 
+%% TODO: insert figure.
+
 The dataset was split 80/10/10 for training/validation/testing. Photos were augmented by displacement and inherently varied by rotation. All images were resized to 224x224 for training.
@@
 
+Further augmentation methods were done for training via contrast, brightness, colorspace, cutout, rotation, sharpness, shearx, inversion, solarization, and translation methods.
+For FixMatch, we followed a standard augmentation pipeline of the above; details can be seen in our github.
+
 \subsection{Fully Supervised Baseline}
@@
 A fully supervised model was implemented using various ResNet/VGG models for the sake of both comparison and as a baseline for our semi-supervised methods.
-After training ResNet18 was determined to be best with a 97\% accuracy on test set after %%TODO: fill in
+After training ResNet18 was determined to be best with a 97.63\% validation accuracy on test set after only 12 epochs.
+
+We achieved this using the pretrained ResNet18 model and fine-tuning it over our dataset.
+Code and parameters can be found in the github repository.
+The primary function of the FS model was to provide a baseline for our semi-supervised methods.
 
@@
 
-\subsubsection{Grad-CAM/Score-CAM}
+We utilized 2 methods of semi-supervised learning: FixMatch and MeanTeacher. Both were supplemented by Grad-CAM
 
-\subsubsection{Fixmatch}
+\subsubsection{Grad-CAM}
+
+Grad-CAM visualizes the last layer of the CNN structure with heatmaps, and is a generalization of the CAM method.
+In the Grad-CAM process, a forward pass is done to compute the class score for target class $c$.
+Then, gradients are backpropagated on the target class score $y^c$ (before softmax), wrt.
+the feature maps of each convolutional layer, $A^k$.
+That is, $\forall k \in \{1, 2, ..., K\}$, we compute the gradient of $\frac{\partial y^c}{A^k}$.
+Then, the importance of the weight $a_k^c\in A^k$ is computed as \begin{align*}
+    a_k^c=\frac{1}{Z}\sum_i\sum_j\frac{\partial y^c}{A_{ij}^k}
+\end{align*} where $Z$ is the total number of spacial locations in the feature map. Then, the final feature map is calculated as \begin{align*}
+    \mathcal{L}_{Grad-CAM}^c=\text{ReLU}\left(\sum_k a_k^cA^k\right)
+\end{align*}
+
+While Grad-CAM can show us the heatmap, the Grad-CAM paper by Selvaraju et al.
+\cite{selvaraju} notes that it lacks the ability to show us the fine grained details like pixel-space gradient visualization, such as Guided Backpropagation.
+
+Guided Backpropagation is a variant of the backpropagation algorithm where negative gradients are suppressed during the backward pass.
+Only positive gradients are propagated, highlighting the pixels in the input image that strongly activate certain neurons in the network.
+This will result in a high-resolution saliency map of the input image.
+To combine it with Grad-CAM, we can multiply the Grad-CAM heatmap with the Guided Backpropagation saliency map element-wise to get the Guided Grad-CAM result.
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.8\linewidth]{gradcam_demo.png}
+    \caption{Grad-CAM visualization demo}
+    \label{fig:gradcam_demo}
+\end{figure}
+%% TODO: insert figure.
+
+\subsubsection{FixMatch}
+
+Our FixMatch model generated pseudo-labels for unlabeled data using weakly augmented data (eg.
+rotation, translation, etc.) and trained to predict these pseudo-labels with strongly augmented data (eg.
+cutout, solarization, color space, etc.).
+
+We trained a variety of different models with different hyperparameters and selected 5 for further testing.
+Parameters can be found on the github in \verb*|dataset/parms.ipynb|.
+All images were standardized at 224x224, using the SyRA synthesized rain test image set with a random augmentation pipeline.
+
+All models were trained for 128 epochs over the WideResNet18 model with depth 16, widen factor 2, and dropout 1.
+Other architectures (within the ResNet family and VGG families) were tried as well.
+The model was trained on the 20 classes of UMD buildings, on Google Colab with a Tesla T4 GPU.
+All code is available on the github repository.
 
@@
 
-\subsection{GNNs/HITL/VQA Experiments}
+Our MeanTeacher model uses consistency regularization that requires 2 models: a student model and a teacher model.
+The teacher model is an exponential moving average of the student model, and the student model is trained to match the teacher model’s predictions.
 
+Our student network acts as the standard neural network, trained on both supervised and unsupervised losses. Our teacher network acts as the target for the student.
+
+For labeled data, the student network is trained to minimize supervised loss via cross-entropy.
+For unlabeled data, the student network is trained to minimize the consistency loss between the student and teacher predictions.
+
+All data went to both of our models, where it was then augmented with random horizontal translations and translations (eg.
+weak augmentation).
+We utilized MSE loss for consistency loss in unlabeled data.
+For labeled data, we utilized the weights formula \begin{align*}
+    \theta_{\text{teacher}}=\alpha \cdot\theta_{\text{teacher}}+(1-\alpha)\cdot\theta_{\text{student}}
+\end{align*} where $\alpha=0.97$ is the decay rate. Final loss was calculated as \begin{align*}
+    \mathcal{L}_{\text{total}}=\mathcal{L}_{\text{supervised}}+\lambda\cdot\mathcal{L}_{\text{consistency}}
+\end{align*}where $\lambda=1.75$ was the weight of the consistency loss.
+
+The model was trained for 25 epochs over the WideResNet18 model.
+The model was trained on the 20 classes of UMD buildings, on Google Colab with a Tesla T4 GPU.
+All code is available on the github repository.
+
+\subsection{GNNs/HITL Experiments}
+
+We additionally experimented with GNNs (Graph Neural Networks), HITL (Human In The Loop), and VQA (Visual Question Answering) methods.
+Results for these can be found in appendix \ref{experiment_results}.
+
+VQA was found to be infeasible due to time constraints; the amount of questions required was too high given our priorities on semi supervised learning and the lack of time we allotted to the experiment.
 % results for these will go into appendix
+
+\subsubsection{HITL}
+
+HITL, or Human In The Loop, is a method to accelerate the training of a model by providing human feedback on the model's predictions.
+This can be used to help the model focus on areas of interest by providing absolute feedback on whether or not Grad-CAM is focusing on the correct areas.
+
+We implemented a model on 9 classes and a train set of 450 images, where humans were asked to provide feedback on the accuracy of class predictions and whether or not the Grad-CAM feedback was accurate (eg.
+not focusing on noise).
+The model was implemented for PyTorch and was trained on Colab with a Tesla T4 GPU for 10 epochs, with human interference once per epoch.
+
+A ResNet18 model was used, with 10 epochs, $lr=0.001$, batch size 64.
 
@@
 
-\subsubsection{HITL}
+Images for GNNs were standardized to 224x224, then ran through our custom implementation of the SLIC Superpixel transform to \verb*|torch_geometric(Data)| objects.
+Edges were generated via a Radius Neighbor Graph with varying parameters.
+The transform method is adapted from low resolution B/W to high resolution color images at variable resolution.
 
-\subsubsection{VQA}
+To visualize the model and SLIC transform, methods were written to represent the graph in 2d space.
 
-\section{Results}
+Our GNN classifier was implemented in PyTorch Geometric, following the method outlined in Long et al \cite{long}.
+The method uses a 3 layer GatConv model with a FC layer at the end.
+The model was initially trained on fully supervised data, but could not complete due to time constraints.
+Training was done on the Columbia \@ SAIL server with an NVIDIA RTX A6000 GPU.
+It is intended to train on 100 epochs, and a hidden dimension of 152.
+
+The SLIC transform results in significant preprocessing costs, and was the main cost of the model. All code is available on the github repository, although no results are provided.
+
+\section{Experiment Results}
 \label{result}
-
-\subsection{Code}
-
-Code for models, data collection and augmentation, along with the SLIC methods and HITL methods, were written and implemented in pytorch and can be found on our Github repository: \url{https://github.com/BlueTurtle123/CMSC472_Final_Project}
+% Demonstrate stats
 
@@
 
+We trained various ResNet/VGG models for the fully supervised baseline.
+After training, ResNet18 was determined to be the best model for semisupervised with a 97.63\% validation accuracy on the test set after 12 epochs.
+All training was done on the 20 classes of UMD buildings, on Google Colab with a Tesla T4 GPU.
+All code is available on the github repository.
+
+All testing was done on the heavily augmented test set to check for robustness, and the table below was generated at 10 epochs.
+
+\begin{table}[H]
+    \centering
+    \begin{tabular}{|c|c|c|}
+        \hline
+        Architecture & Val Accuracy & Test Accuracy \\
+        \hline
+        DenseNet121 & 97.47\% & 87.77\% \\
+        \hline
+        DenseNet201 & 95.26\% & 87.93\% \\
+        \hline
+        ResNet18 & 97.63\% & 88.54\% \\
+        \hline
+        ResNet34 & 98.89\% & 86.38\% \\
+        \hline
+        ResNet50 & 96.05\% & 80.13\% \\
+        \hline
+    \end{tabular}
+    \caption{Comparison of DenseNet/ResNet Model Accuracies}
+    \label{tab:dnrn_model_accuracies}
+\end{table}
+
+The following VGG/VIT models were also tested, but were found to be less effective than the ResNet models.
+
+\begin{table}[H]
+    \centering
+    \begin{tabular}{|c|c|c|}
+        \hline
+        Architecture & Val Accuracy & Test Accuracy \\
+        \hline
+        VGG11 & 84.36\% & 55.73\% \\
+        \hline
+        VGG16 & 79.94\% & 78.84\% \\
+        \hline
+        VGG19 & 80.09\% & 41.33\% \\
+        \hline
+        Vit16\_224 & 69.04\% & 42.62\% \\
+        \hline
+    \end{tabular}
+    \caption{Comparison of VGG/VIT Model Accuracies}
+    \label{tab:vgg_model_accuracies}
+\end{table}
+\subsection{Semi-Supervised Methods}
+\subsubsection{FixMatch}
+
+Our FixMatch method achieved peak top1 accuracy of 40.45\% and top5 accuracy of 75.44\%, where top1 indicates a correct guess within the most confident prediction and top5 indicating a correct guess on the top 5 most confident predictions.
+
+\begin{table}[H]
+    \centering
+    \begin{tabular}{|c|c|c|}
+        \hline
+        Model & Top-1 Accuracy & Top-5 Accuracy \\
+        \hline
+        1 & 27.95\% & 61.25\% \\
+        \hline
+        2 & 30.44\% & 64.50\% \\
+        \hline
+        3 & 38.75\% & 75.08\% \\
+        \hline
+        4 & 40.45\% & 75.44\% \\
+        \hline
+        5 & 19.20\% & 68.37\% \\
+        \hline
+    \end{tabular}
+    \caption{Comparison of Model Accuracies}
+    \label{tab:fm_model_accuracies}
+\end{table}
+
+The FixMatch model fell into the issue of overfitting on our dataset fairly quickly due to the relatively small per-class dataset.
+This was exacerbated by the limited weather conditions and time of day we took photos, which resulted in a lack of diversity and strong overfitting on nonexistent features.
+
+However, we were successful in locking Grad-CAM onto building features, and we achieved reasonable test accuracies on the heavily augmented SyRA test set.
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.8\linewidth]{fixmatch.png}
+    \caption{FixMatch Model Grad-CAM visualization}
+    \label{fig:fixmatch_results}
+\end{figure}
+
+\subsubsection{MeanTeacher}
+
+Our MeanTeacher model achieved top1 student accuracy of 75.08\% and top1 teacher accuracy of 73.89\%.
+This utilized $\lambda=1.5, \alpha=.99$, with batch size $0.001$, SGD decay $10^{-4}$, and momentum $.9$ over 20 epochs.
+
+The MeanTeacher model performed significantly better than the FixMatch model due to its consistency regularization.
+The model was able to generalize better to the test set and was less prone to overfitting.
+
+However, it still suffered from the same lack of diversity.
+Once again, we were successful in locking Grad-CAM onto building features, and we achieved reasonable test accuracies on the heavily augmented SyRA test set.
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[trim={0 38cm 0 12.5cm},clip,width=0.6\linewidth]{meanteacher.png}
+    \caption{MeanTeacher Model Grad-CAM visualization}
+    \label{fig:meanteacher_results}
+\end{figure}
 % Demonstrate stats
 
-\subsection{Semi-Supervised Methods}
+\section{Conclusion}
 
-% Demonstrate stats
+Our key findings are that for the classification of buildings, ResNet18 is the best baseline model; and that MeanTeacher outperformed FixMatch considerably, achieving a top1 student accuracy of 75.08\% and top1 teacher accuracy of 73.89\%.
+Extensive quantitative findings prove that it's also much more robust to overfitting than FixMatch, and reacts better to an augmented test set.
+For both, we were successful in locking Grad-CAM onto building features.
 
-\subsection{Other Experiments}
+However, both models suffered from a lack of diversity in the dataset, which led to overfitting on nonexistent features and a lack of improvement.
+This was exacerbated by the limited weather conditions and time of day we took photos, which resulted in a lack of diversity and strong overfitting on nonexistent features.
+Additionally, weather augmentation was not as diverse as might be necessary to prove robustness to real world conditions.
 
-\subsubsection{HITL}
+Future research will focus on increasing the diversity of the dataset, along with continuing preliminary work on GNNs.
 
-\subsubsection{GNN SLIC Transform}
+\subsection*{GitHub Repository}
 
-% quick overview of new transform and then note results in appendix
-
-\subsubsection{VQA}
-
-% quick overview of VQA and then note results in appendix
+All code and resources for this project are available at: \url{https://github.com/BlueTurtle123/CMSC472_Final_Project}
 
@@
 
-\section{Extra Figures}
+\section{Extra Experiment Results}
+\label{experiment_results}
+
+\subsection{HITL}
+
+After 10 epochs, the model achieved training accuracy $93.74\%$, and test accuracy $67.6\%$.
 
@@
     \centering
-    \includegraphics[width=1\linewidth]{fig2.png}
-    \caption{Preliminary Results with structure from ResNet}
-    \label{fig:prelim_results_2}
+    \includegraphics[width=0.8\linewidth]{hitl.png}
+    \caption{HITL Model Grad-CAM visualization}
+    \label{fig:hitl_results}
 \end{figure}
+
+\subsection{GNNs}
+
+The GNN model was unable to complete training due to time constraints. However, we did complete our SLIC transform, for which we have the following figures:
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.8\linewidth]{slic_1.png}
+    \caption{SLIC transform of Art-Sociology building picture}
+    \label{fig:slic1}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.8\linewidth]{slic_2.png}
+    \caption{SLIC transform of Iribe building picture}
+    \label{fig:slic2}
+\end{figure}
+
+Note how in the pictures, excessive complexity is granted to largely irrelevant details, such as the clouds and sky.
+Minute differences in the image data due to noise result in a lack of clustering in those areas.
+
+\section{Extra Figures}
+\label{extra_figures}
 

### 2024-12-09 report/paper/draft.tex
minor edits

@@
 
-We trained a variety of different models with different hyperparameters and selected 5 for further testing.
+We trained a variety of different models with different hyperparameters (batch size, momentum, warm up epochs, pseudo label threshold, etc) and selected 5 for further testing.
 Parameters can be found on the github in \verb*|dataset/parms.ipynb|.
@@
 The model was implemented for PyTorch and was trained on Colab with a Tesla T4 GPU for 10 epochs, with human interference once per epoch.
+
+After each epoch, the human was asked to confirm or deny the accuracy of the model's prediction, and asked a region of the image for the model to focus on more based on the Grad-CAM feedback.
 
@@
 However, both models suffered from a lack of diversity in the dataset, which led to overfitting on nonexistent features and a lack of improvement.
-This was exacerbated by the limited weather conditions and time of day we took photos, which resulted in a lack of diversity and strong overfitting on nonexistent features.
-Additionally, weather augmentation was not as diverse as might be necessary to prove robustness to real world conditions.
+Advancement on FixMatch can be achieved via cleaning up the dataset (eg less noise).
+Additionally, multiple classes can be defined for various parts of buildings (i.e.
+Atlantic Building looks very different depending on the angle)
 

### 2024-12-09 report/paper/draft.tex
an error correction
revisions

@@
 
+% All packages added by Jeffery
 \usepackage{graphicx} % Required for inserting images
@@
 \usepackage[shortlabels]{enumitem}
+\usepackage{subcaption}
 
@@
 Grad-CAM++ can be used as an important means for highlighting image classification confidence, both of which we intend to use as the most advanced methods in their respective lineages.
-As an example, see our preliminary original Grad-CAM results in Figure 1 on instances on our test set, where Grad-CAM indicates it's making predictions based on unrelated objects (foreground foliage, people, unrelated elements of the building).
+As an example, see our Grad-CAM results in Appendix \ref{extra_figures} on instances on our test set.
 This can be used for confirmation of model confidence.
@@
 We took around 4000 photos of UMD buildings over 20 classes, aiming for a 60/40 split of daytime/nighttime photos.
+Buildings included a diverse set of buildings but also included 4 dorms of extremely similar construction.
 
@@
 We achieved this using the pretrained ResNet18 model and fine-tuning it over our dataset.
-Code and parameters can be found in the github repository.
+Code and parameters can be found in the Github repository.
 The primary function of the FS model was to provide a baseline for our semi-supervised methods.
@@
 
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.8\linewidth]{model_architecture.png}
+    \caption{Grad-CAM Model Architecture}
+    \label{fig:gradcam_architecture}
+\end{figure}
+
 Guided Backpropagation is a variant of the backpropagation algorithm where negative gradients are suppressed during the backward pass.
@@
 We trained a variety of different models with different hyperparameters (batch size, momentum, warm up epochs, pseudo label threshold, etc) and selected 5 for further testing.
-Parameters can be found on the github in \verb*|dataset/parms.ipynb|.
+Parameters can be found on the github in \verb*|CMSC472_Final_Project/code/my_fixmatch/dataset/parms.ipynb|.
 All images were standardized at 224x224, using the SyRA synthesized rain test image set with a random augmentation pipeline.
 
-All models were trained for 128 epochs over the WideResNet18 model with depth 16, widen factor 2, and dropout 1.
-Other architectures (within the ResNet family and VGG families) were tried as well.
-The model was trained on the 20 classes of UMD buildings, on Google Colab with a Tesla T4 GPU.
-All code is available on the github repository.
+Models 1, 2, 3 were trained for 128 epochs, and 4, 5 for 32 over the WideResNet model with depth 16, widen factor 2, and dropout 1.
+Each model was trained on the previous, iteratively.
+The model was trained on the 20 classes of UMD buildings, on a NVIDIA RTX 3090.
+All code is available on the Github repository.
 
@@
     \theta_{\text{teacher}}=\alpha \cdot\theta_{\text{teacher}}+(1-\alpha)\cdot\theta_{\text{student}}
-\end{align*} where $\alpha=0.97$ is the decay rate. Final loss was calculated as \begin{align*}
+\end{align*} where $\alpha$ is the decay rate. Final loss was calculated as \begin{align*}
     \mathcal{L}_{\text{total}}=\mathcal{L}_{\text{supervised}}+\lambda\cdot\mathcal{L}_{\text{consistency}}
-\end{align*}where $\lambda=1.75$ was the weight of the consistency loss.
+\end{align*}where $\lambda$ was the weight of the consistency loss.
 
-The model was trained for 25 epochs over the WideResNet18 model.
+The model was trained for 25 epochs over the ResNet18 model.
 The model was trained on the 20 classes of UMD buildings, on Google Colab with a Tesla T4 GPU.
-All code is available on the github repository.
+All code is available on the Github repository.
 
@@
 
-VQA was found to be infeasible due to time constraints; the amount of questions required was too high given our priorities on semi supervised learning and the lack of time we allotted to the experiment.
+VQA was found to be infeasible due to time constraints; the amount of questions required was too high given our priorities on semi-supervised learning and the lack of time we allotted to the experiment.
 % results for these will go into appendix
@@
 
-The SLIC transform results in significant preprocessing costs, and was the main cost of the model. All code is available on the github repository, although no results are provided.
+The SLIC transform results in significant preprocessing costs, and was the main cost of the model. All code is available on the Github repository, although no results are provided.
 
@@
 All training was done on the 20 classes of UMD buildings, on Google Colab with a Tesla T4 GPU.
-All code is available on the github repository.
+All code is available on the Github repository.
 
-All testing was done on the heavily augmented test set to check for robustness, and the table below was generated at 10 epochs.
+All testing was done on the heavily augmented test set to check for robustness, and we achieved the following peak accuracies for the models within 25 epochs:
 
@@
         \hline
-        Architecture & Val Accuracy & Test Accuracy \\
+        Architecture & Best Val Accuracy & Test Accuracy \\
         \hline
-        DenseNet121 & 97.47\% & 87.77\% \\
+        DenseNet121 & 98.26\% & 87.77\% \\
         \hline
-        DenseNet201 & 95.26\% & 87.93\% \\
+        DenseNet201 & 97.00\% & 87.93\% \\
         \hline
@@
 However, we were successful in locking Grad-CAM onto building features, and we achieved reasonable test accuracies on the heavily augmented SyRA test set.
+If time permits, we would like to add more labeled data to the dataset and see if the result improves.
 
@@
 Our MeanTeacher model achieved top1 student accuracy of 75.08\% and top1 teacher accuracy of 73.89\%.
-This utilized $\lambda=1.5, \alpha=.99$, with batch size $0.001$, SGD decay $10^{-4}$, and momentum $.9$ over 20 epochs.
+This utilized $\lambda=1.5, \alpha=.99$, with $lr=0.001$, batch size $128$, SGD decay $10^{-4}$, and momentum $.9$ over 20 epochs.
 
@@
 Future research will focus on increasing the diversity of the dataset, along with continuing preliminary work on GNNs.
+We would also like to experiment with more fine tuning of parameters and warm up functions.
 
@@
 
+\begin{figure}[H]
+    \centering
+    % First subfigure
+    \begin{subfigure}[b]{0.45\linewidth}
+        \centering
+        \includegraphics[width=\linewidth]{new_gradcam_result2.png}
+        \caption{Grad-CAM visualization on ResNet18}
+        \label{fig:gradcam1}
+    \end{subfigure}
+    \hfill  % Adds horizontal spacing
+    % Second subfigure
+    \begin{subfigure}[b]{0.45\linewidth}
+        \centering
+        \includegraphics[width=\linewidth]{new_gradcam_plusplus_result2.png}
+        \caption{Grad-CAM++ visualization on ResNet18}
+        \label{fig:gradcam2}
+    \end{subfigure}
+
+    \caption{Comparison of Grad-CAM and Grad-CAM++ visualizations on ResNet18}
+    \label{fig:gradcam_comparison1}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
+    % First subfigure
+    \begin{subfigure}[b]{0.45\linewidth}
+        \centering
+        \includegraphics[width=\linewidth]{gradcam_result3.png}
+        \caption{Grad-CAM visualization on MeanTeach}
+        \label{fig:gradcam3}
+    \end{subfigure}
+    \hfill  % Adds horizontal spacing
+    % Second subfigure
+    \begin{subfigure}[b]{0.45\linewidth}
+        \centering
+        \includegraphics[width=\linewidth]{mean_teach_gradcam_plusplus.png}
+        \caption{Grad-CAM++ visualization on MeanTeach}
+        \label{fig:gradcam4}
+    \end{subfigure}
+
+    \caption{Comparison of Grad-CAM and Grad-CAM++ visualizations on MeanTeach}
+    \label{fig:gradcam_comparison2}
+\end{figure}
+
 \medskip

### 2024-12-09 report/paper/draft.tex
revisions v2

@@
 %% TODO: insert figure.
+Grad-CAM++ works by assigning importance weights to individual pixels in the feature maps, rather than the global pooled gradients used in Grad-CAM, allowing it to better capture fine-grained details and spatial information.
+This pixel-level weighting enables Grad-CAM++ to provide more localized and precise visual explanations, especially in cases where multiple instances of the same class are present in an image.
+Despite this theoretical improvement, the results we obtained did not show significant differences compared to Grad-CAM, potentially due to limitations in model architecture, dataset complexity, or specific implementation nuances.
 
@@
 
-Models 1, 2, 3 were trained for 128 epochs, and 4, 5 for 32 over the WideResNet model with depth 16, widen factor 2, and dropout 1.
+Models 1, 2 were trained for 128 epochs, and 3, 4, 5 for 32 over the WideResNet model with depth 16, widen factor 2, and dropout 1.
 Each model was trained on the previous, iteratively.
@@
 Additionally, multiple classes can be defined for various parts of buildings (i.e.
-Atlantic Building looks very different depending on the angle)
+Atlantic Building looks very different depending on the angle).
+
+For our dataset, after trying various network architectures, we learned that having deep layers won’t simply improve the prediction accuracy (and can easily result in overfitting).
+In the ResNet family, for example, ResNet50 performed less accurately compared to ResNet18.
+Another interesting result we got is that in the VGG family, the test data showed us that VGG16 > VGG11 > VGG19 accuracy-wise.
+Thus, networks with not enough layers can also cause a difference.
 

### 2024-12-09 report/paper/draft.tex
draft final check

@@
     With the rise of new computational architectures for image processing and classification, computer vision systems are highly diverse, raising the question of which approach is the most effective for a given task.
-Our study focuses on designing and evaluating a reliable classification system for identifying buildings on the University of Maryland campus using semi-supervised CNN.
-By constructing a custom image database from scratch and experimenting with various architectures for semi-supervised learning, we aim to identify the best model for our classification problem.
-Additionally, we utilize CNN visualization eg.
-Grad-CAM to further assess our model’s performance.
+Our study focuses on designing and evaluating a classification system for identifying buildings on the University of Maryland campus using convolutional neural networks.
+By experimenting with various architectures from both supervised and semi-supervised learning, we found that the ResNet-18 architecture works the best in our use case.
+We also tested using Human-in-Loop Learning with Grad-CAM to get a more accurate depiction of which parts of the images are most important for classification.
 \end{abstract}
@@
 We additionally worked with implementation of high resolution images on limited datasets to semi-supervised methods, along with the use of Grad-CAM for image segmentation.
+
+Semi-supervised learning is often chosen over supervised learning when labeled data is limited and costly, while unlabeled data is more readily available and cheaper.
+Semi-supervised learning can enhance model performance and generalization by leveraging both labeled and unlabeled data.
+This approach is particularly advantageous in real-world scenarios where gathering extensive labeled datasets is impractical.
+
+Labeling every image in an extremely large dataset is unrealistic in a real-world scenario.
+So, labeling a small portion of the dataset and creating pseudo-labels of the unlabeled training set is more efficient.
 
@@
 
-Future research will focus on increasing the diversity of the dataset, along with continuing preliminary work on GNNs.
+\subsection*{Future Work}
+
+In the short term, research would primarily focus on increasing the diversity of the dataset.
+It would be ideal to have, additionally, a much cleaner dataset for the FixMatch model, and to have more classes defined for the buildings.
+
 We would also like to experiment with more fine tuning of parameters and warm up functions.
+
+The primary long term goals of the project would be optimizing the MeanTeacher model to achieve higher accuracy, and to experiment with more advanced methods of semi-supervised learning.
+Although we believe that one method of achieving this is via diversity on the dataset, another method is to use more powerful computing resources given the low amount of epochs we were able to achieve given our technical constraints.
+
+An interesting advanced method of semi-supervised learning would be to utilize Grad-CAM as a primary method of segmentation, which would be a major innovation in the field; additionally, utilizing Grad-CAM as a secondary target (where a fully labeled result might use a fully masked image as GT) could result in much stronger semi-supervised results.
+
+We would also like to continue our novel work on GNNs for large images in color.
+No significant results in the scientific community have passed with regards to GNN image recognition on high resolution color images, and we believe that this could be a significant area of research.
 
@@
 
-All code and resources for this project are available at: \url{https://github.com/BlueTurtle123/CMSC472_Final_Project}
+All code and resources for this project are available at: \url{https://github.com/BlueTurtle123/CMSC472_Final_Project}, and the image data is available upon request to \verb*|jtian12@umd.edu|
 

### 2024-12-09 report/paper/draft.tex
draft final final check

@@
 
-From these prior works we have the basic motivation of leveraging traditional CNN image segmentation and recognition techniques for the sake of identifying any buildings in the input images.
-Our main innovation is to attempt to use Grad-CAM++ or a similar technique to see if they can be used for image segmentation instead, and to attempt to apply this basic system to a variety of goals.
+From these prior works we have the basic motivation of leveraging traditional CNN image recognition techniques for the sake of identifying any buildings in the input images.
+Our main innovation is to attempt to use Grad-CAM++ or a similar technique to see if they can be used for helping improve recognition instead, and to attempt to apply this basic system to a variety of goals.
+
+We use Grad-CAM because we need a way to visualize the convolutional layers to help guide a semi-supervised model.
+If we look at the Fully Connected (FC) layers, the feature maps get flattened into a 1-D vector, which loses the spatial information inherent in the earlier convolutional layers, so it is not the place we should be looking for.
+Grad-CAM is thus a method of visualizing the convolutional layers, and can be used to help guide the model to focus on the building itself.
 
@@
     \centering
-    \includegraphics[width=0.8\linewidth]{fixmatch.png}
+    \includegraphics[width=0.6\linewidth]{fixmatch.png}
     \caption{FixMatch Model Grad-CAM visualization}
@@
     \centering
-    \includegraphics[trim={0 38cm 0 12.5cm},clip,width=0.6\linewidth]{meanteacher.png}
+    \includegraphics[trim={0 38cm 0 12.7cm},clip,width=0.6\linewidth]{meanteacher.png}
     \caption{MeanTeacher Model Grad-CAM visualization}
@@
 
+\subsection*{Presentation}
+
+A presentation of this project is available at: \url{https://docs.google.com/presentation/d/1SDHgrbd2Suk2Qw0XBbqwSBKSYyZ87k4XBCzELvPUu8c/edit?usp=sharing}
+
 \newpage 
@@
 \end{figure}
-
-Note how in the pictures, excessive complexity is granted to largely irrelevant details, such as the clouds and sky.
-Minute differences in the image data due to noise result in a lack of clustering in those areas.
 
